---
title: "Dev history - Renv"
output: 
  html_document:
    toc: true
    toc_depth: 1
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  eval = FALSE
  )
```

In this document, you will find the important steps/commands to use {renv} in a package (initialization, daily use,...)

# Start {renv} the first time

```{r}
renv::init()
```

# Set RENV cache 

Recommend setting a global variable: RENV_PATHS_CACHE
With cache path where to store all R packages, between projects 

```{r}
# usethis::edit_r_environ(scope = "project")
```

=> Restart session
Tell all contributors to set this Environment variable

You may need to verify not empty

```{r}
# Sys.getenv("RENV_PATHS_CACHE")
```


# Rprofile

Add the following lines to your .Rprofile in the project
- On modifie le ".Rprofile" pour
  - figer les depot CRAN et leur nom
  - forcer l'utilisation du cache partagé {renv}
  - mettre en adéquation les depot d'installation et ceux du renv.lock

```{r}
# Sourcing user .Rprofile if it exists
home_profile <- file.path(
  Sys.getenv("HOME"),
  ".Rprofile"
)
if (file.exists(home_profile)){
  source(home_profile)
}

options(renv.config.pak.enabled = TRUE)

# Fix CRAN version
source("renv/activate.R")
lock_ <- renv:::lockfile(file = "renv.lock")
#
if (grepl("ubuntu 18.04|debian 8", tolower(utils::osVersion))) {
  repos <- c("RSPM" = "https://packagemanager.rstudio.com/all/__linux__/bionic/latest",
             "thinkropen" = "https://thinkr-open.r-universe.dev",
             "CRAN" = "https://cran.rstudio.com")
} else if (grepl("ubuntu 20.04|debian 9", tolower(utils::osVersion))) {
  repos <- c("RSPM" = "https://packagemanager.rstudio.com/all/__linux__/focal/latest",
             "thinkropen" = "https://thinkr-open.r-universe.dev",
             "CRAN" = "https://cran.rstudio.com")
} else if (grepl("centos", tolower(utils::osVersion))) {
  # Important for MacOS users in particular
  repos <- c("RSPM" = "https://packagemanager.rstudio.com/all/__linux__/centos7/latest",
             "thinkropen" = "https://thinkr-open.r-universe.dev",
             "CRAN" = "https://cran.rstudio.com")
} else {
  # Important for MacOS and Windows users in particular
  repos <- c("CRAN" = "https://cran.rstudio.com",
             "RSPM" = "https://cran.rstudio.com",
             "thinkropen" = "https://thinkr-open.r-universe.dev")
}


lock_$repos(.repos = repos)
options(repos = repos)


lock_$write(file = "renv.lock")
rm(lock_)
rm(repos)


renv::activate()

# cache ----
 renv::settings$use.cache(TRUE)

# Setting shiny.autoload.r to FALSE

options(shiny.autoload.r = FALSE)
```

=> Restart RStudio Session

# renv.lock

You may need to verify renv.lock with:
 "Name": "REPO_NAME",
 "URL": "https://packagemanager.rstudio.com/all/latest"

# Install from CRAN

```{r}

install.packages("rstudioapi", repos = getOption("repos")["CRAN"])
install.packages("remotes", repos = getOption("repos")["CRAN"])
remotes::install_cran("devtools", repos = getOption("repos")["CRAN"])

# If needed --
# remotes::install_cran("golem", repos = getOption("repos")["CRAN"])
# remotes::install_cran("shiny", repos = getOption("repos")["CRAN"])

# Install from GitHub through r-universe first --
# remotes::install_cran("attachment", repos = getOption("repos")[c("thinkropen", "CRAN")])

remotes::install_cran("fusen", repos = getOption("repos")[c("thinkropen", "CRAN")])
remotes::install_cran("checkhelper", repos = getOption("repos")[c("thinkropen", "CRAN")])
remotes::install_cran("thinkrtemplate", repos = getOption("repos")[c("thinkropen", "CRAN")])
```
