---
title: "Dev history - Package"
output: 
  html_document:
    toc: true
    toc_depth: 1
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  eval = FALSE
  )
```

```{r}
# install.packages("remotes")
remotes::install_github(repo = "Thinkr-open/papillon")
install.packages('checkhelper', repos = 'https://thinkr-open.r-universe.dev')
```


In this document, you will find the useful steps/commands to start the development of a package (structure, documentation, ...)

# At the beggining of the developments
## Set the dev tools

### Add git templates

```{r}
# GitLab MR and git commit templates
lozen::add_git_templates()
```

### Add kit package

```{r}
lozen::add_kit_package(type = c("package", "deliverables"))
lozen::add_kit_project(name_licence = "Exemple", type_licence = usethis::use_mit_license)
```

### Create a `inst` dir

```{r}
dir.create("inst")
```

### Hide some files in .Rbuildignore and .gitignore

```{r}
usethis::use_build_ignore("dev")
usethis::use_build_ignore("ci/lib")
usethis::use_build_ignore("rsconnect")

usethis::use_git_ignore("docs/")
usethis::use_git_ignore("rsconnect/")
usethis::git_vaccinate()
usethis::use_git_ignore(c(".DS_Store", ".Rproj.user", ".Rdata", ".Rhistory", ".httr-oauth"))
```

### Add some required packages

```{r}
# Pipe ----
usethis::use_pipe()
# _Tests ----
usethis::use_testthat()
```

### Set the CI

```{r}
# _CI (cf {gitlabr} templates) ----
lozen::use_gitlab_ci(image = "rocker/verse",
                              gitlab_url = Sys.getenv("GITLAB_URL"),
                              repo_name = "https://packagemanager.rstudio.com/all/__linux__/focal/latest",
                              type = "check-coverage-pkgdown")

# GitHub Actions ----
# usethis::use_github_action_check_standard()
# usethis::use_github_action("pkgdown")
# usethis::use_github_action("test-coverage")
```

## Add general information/documentation about the package

### Update DESCRIPTION

```{r}
library(desc)
unlink("DESCRIPTION")

my_desc <- description$new("!new")
my_desc$set_version("0.0.0.9000")
my_desc$set(Package = "dummypackage")
my_desc$set(Title = "Some random package")
my_desc$set(Description = "A random package.")
my_desc$set(
  "Authors@R",
  'c(
  person("John", "Doe", email = "john@doe.com", role = c("aut", "cre"))
)'
)
my_desc$set("VignetteBuilder", "knitr")
my_desc$del("Maintainer")
my_desc$del("URL")
my_desc$del("BugReports")
my_desc$write(file = "DESCRIPTION")
```

### Licence

```{r}
usethis::use_proprietary_license("MyCompany")
```

### README

```{r}
#usethis::use_readme_rmd()
papillon::generate_readme_rmd()
papillon::generate_readme_rmd(parts = "description")
```

### NEWS

```{r}
usethis::use_news_md()
```

### Code of conduct

```{r}
usethis::use_code_of_conduct()
```

### Contributing guide

```{r}
usethis::use_tidy_contributing()
```

### Package-level documentation

```{r}
usethis::use_package_doc()
```


### Description and Bibliography

```{r}
papillon::create_pkg_desc_file(out.dir = "inst", source = c("archive"), to = "html")
```

## Tools to help to resolve issues

```{r}
# Get global variables
checkhelper::print_globals()
# Hexadecimal translation of an accent - if there are notes about non ASCII characters
stringi::stri_trans_general("é", "hex")
```

