---
title: "Dev history - Package"
output: 
  html_document:
    toc: true
    toc_depth: 1
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  eval = FALSE
)
```

In this document, you will find the useful steps/commands to start the development of a package (structure, documentation, ...)

# At the beggining of the developments
## Set the dev tools

### Add git templates

```{r}
# GitLab MR and git commit templates
lozen::add_git_templates()
```

### Hide some files in .Rbuildignore and .gitignore

```{r}
usethis::use_build_ignore("dev")
usethis::use_build_ignore("ci/lib")
usethis::use_build_ignore("rsconnect")

usethis::use_git_ignore("docs/")
usethis::use_git_ignore("rsconnect/")
usethis::git_vaccinate()
usethis::use_git_ignore(c(".DS_Store", ".Rproj.user", ".Rdata", ".Rhistory", ".httr-oauth"))
```

### Add some required packages

```{r}
# Pipe ----
usethis::use_pipe()
# _Tests ----
usethis::use_testthat()
```

### Set the CI

```{r}
# _CI (cf {gitlabr} templates) ----
lozen::use_gitlab_ci(
  image = "rocker/verse",
  gitlab_url = Sys.getenv("GITLAB_URL", unset = "https://gitlab.com"),
  repo_name = "https://packagemanager.rstudio.com/all/__linux__/focal/latest",
  type = "check-coverage-pkgdown"
)
```

## Add general information/documentation about the package

### Update DESCRIPTION

```{r}
library(desc)
unlink("DESCRIPTION")

my_desc <- description$new("!new")
my_desc$set_version("0.0.0.9000")
my_desc$set(Package = "deeptools")
my_desc$set(Title = "Tools to analyze video images")
my_desc$set(Description = "Images were analyzed in a game. This package explores the results of the game.")
my_desc$set(
  "Authors@R",
  'c(
  person("Sebastien", "Rochette", email = "sebastien@thinkr.fr", role = c("aut", "cre"), comment = c(ORCID = "0000-0002-1565-9313")),
  person("Colin", "Fay", email = "colin@thinkr.fr", role = c("aut"), comment = c(ORCID = "0000-0001-7343-1846")),
  person("Vincent", "Guyader", email = "vincent@thinkr.fr", role = c("aut"), comment = c(ORCID = "0000-0003-0671-9270")),
  person(given = "ThinkR", role = "cph")
)'
)
my_desc$set("VignetteBuilder", "knitr")
my_desc$del("Maintainer")
my_desc$del("URL")
my_desc$del("BugReports")
my_desc$write(file = "DESCRIPTION")
```

### Licence

```{r}
usethis::use_proprietary_license("ThinkR")
# usethis::use_mit_license("ThinkR")
```

### README

```{r}
usethis::use_readme_rmd()
papillon::generate_readme_rmd()
papillon::generate_readme_rmd(parts = "description")

# _Badges GitLab
usethis::use_badge(
  badge_name = "pipeline status",
  href = "https://gitlab.com/<group>/<project>/-/commits/main",
  src = "https://gitlab.com/<group>/<project>/badges/main/pipeline.svg"
)
usethis::use_badge(
  badge_name = "coverage report",
  href = "http://<group>.pages.gitlab.com/<project>/coverage.html",
  src = "https://gitlab.com/<group>/<project>/badges/main/coverage.svg"
)
```

### NEWS

```{r}
usethis::use_news_md()
```

### Code of conduct

```{r}
usethis::use_code_of_conduct(contact = "contact@think.fr")
```

### Contributing guide

```{r}
usethis::use_tidy_contributing()
```

### Package-level documentation

```{r}
usethis::use_package_doc()
```

### Add a css for the vignettes

```{r}
file.copy(
  system.file("templates/html/header_hide.html", package = "lozen"),
  "vignettes"
)
lozen::add_thinkr_css(path = "../vignettes/")
```

### Description and Bibliography

```{r}
papillon::create_pkg_desc_file(out.dir = "inst", source = c("archive"), to = "html")
lozen::create_pkg_biblio_file_thinkr()
```

## Tools to help to resolve issues

```{r}
# Get global variables
checkhelper::print_globals()
# Hexadecimal translation of an accent - if there are notes about non ASCII characters
stringi::stri_trans_general("é", "hex")
```



# Each time, before pushing to the server

## Inflate all flat files to be up-to-date

Be sure to inflate all flat files before to update the documentation and run the check.

```{r}
# voir fusen::inflate_all()
```

## Update the documentation with `{attachment}`

```{r}
# install.packages("attachment",
#                  repos = "https://thinkr-open.r-universe.dev/")

suggests <- c(
  "bookdown",
  "renv",
  "remotes",
  "covr",
  "gitdown",
  "testdown",
  "thinkrtemplate",
  "devtools",
  "git2r",
  "DT",
  "htmltools",
  "markdown",
  "fusen"
)
attachment::att_amend_desc(
  pkg_ignore = suggests,
  extra.suggests = suggests
)
attachment::set_remotes_to_desc()

desc::desc_bump_version(which = "dev")
```

## Check the package

```{r}
# devtools::test()
# devtools::check()
# devtools::check(args = c("--no-examples", "--no-vignettes", "--no-tests"),
#                 build_args = "--no-build-vignettes")
devtools::check(
  args = c("--no-vignettes"),
  build_args = "--no-build-vignettes"
)
check_n_covr <- function() {
  res <- devtools::check(args = c("--no-tests"))
  print(res)
  covr::package_coverage(type = "tests", quiet = TRUE)
}
check_n_covr()
```
