---
title: "flat_manage_gitlab_projects.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

<!--
 You need to run the 'description' chunk in the '0-dev_history.Rmd' file before continuing your code there.
-->

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

# Create the project

# `create_group_project()`: Create a new project

Define:

- The name of the project you want to create in `project_name` *(choose it as for package name. No special character, only dot if needed)*
- The `namespace_id` of the group where you want to create your project

```{r function-create_group_project}
#' Create new project in a group
#'
#' @param project_name name of the project to create
#' @param namespace_id id of the group in which to add the project
#' @param gitlab_con Connection credentials to GitLab.
#'  Better use `set_gitlab_connection()` before this function
#' @param default_branch Default branch for the project created. Default to "main".
#'
#' @return project_id. Side effect: Create a project on GitLab if not exists.
#' @importFrom gitlabr gitlab
#' @importFrom dplyr filter pull
#' @export
#'
create_group_project <- function(project_name, namespace_id, gitlab_con = "default", default_branch = "main") {

  if (!is.null(namespace_id)) {

    group_projects <- gitlab(req = paste0("groups/", namespace_id, "/projects"),
                             verb = httr::GET, gitlab_con = gitlab_con)

    if (project_name %in% group_projects[["name"]]) {
      project_id <- filter(group_projects, name == project_name)[["id"]]

      message("Project: \'", project_name, "\' already exists in group: ",
              namespace_id,
              # filter(all_groups, id == namespace_id)[["name"]],
              ". ",
              "Using project_id: ", project_id)

    } else {
      # Create project
      my_project <- gitlab(req = "projects", name = project_name,
                           namespace_id = namespace_id,
                           default_branch = default_branch,
                           initialize_with_readme = FALSE,
                           verb = httr::POST, gitlab_con = gitlab_con)
      project_id <- my_project$id
      message("New project created: ", project_id)
    }

  } else {

    user_id <- gitlab(req = paste0("user"),
                      verb = httr::GET, gitlab_con = gitlab_con) %>%
      pull(id)

    user_projects <- gitlab(req = paste0("users/", user_id, "/projects"),
                            verb = httr::GET, gitlab_con = gitlab_con)

    if (project_name %in% user_projects[["name"]]) {
      project_id <- filter(user_projects, name == project_name)[["id"]]

      message("Project: \'", project_name, "\' already exists in your personal namespace",
              # filter(all_groups, id == namespace_id)[["name"]],
              ". ",
              "Using project_id: ", project_id)

    } else {
      # Create project
      my_project <- gitlab(req = "projects", name = project_name,
                           namespace_id = NULL,
                           default_branch = default_branch,
                           initialize_with_readme = FALSE,
                           verb = httr::POST, gitlab_con = gitlab_con)
      project_id <- my_project$id
      message("New project created: ", project_id)
    }

  }

  as.numeric(project_id)
}

```
  
```{r example-create_group_project, eval = FALSE}
#' \dontrun{
create_group_project(
  project_name = project_name, 
  namespace_id = namespace_id, 
  default_branch = "main"
)
#' }
```
  
```{r tests-create_group_project}
test_that("create_group_project works", {

})
```

# `protect_branches()`: Protect branches

```{r function-protect_branches}
#' Protect 'main' and 'production' from push on server
#'
#' @param project_id project_id
#' @param unprotect Logical. Whether to unprotect branches or not.
#'
#' @return Side effect: Branches protected from push on server.
#' @importFrom gitlabr gitlab
#' @export
#'
protect_branches <- function(project_id, unprotect = FALSE) {

  p_branches <- gitlab(req = paste0("projects/", project_id, "/protected_branches"),
                       verb = httr::GET)

  # Delete master protection if exists
  if (nrow(p_branches) != 0 && "master" %in% p_branches[["name"]]) {
    gitlab(req = paste0("projects/", project_id, "/protected_branches/master"),
           verb = httr::DELETE)
  }

  # Add master protection
  protect_master <- gitlab(req = paste0("projects/", project_id, "/protected_branches"),
                           verb = httr::POST,
                           name = "master",
                           push_access_level = ifelse(isTRUE(unprotect), 40, 0),
                           merge_access_level = 40 # Maintainers
  )
  message("\'master\'", ifelse(isTRUE(unprotect), " not ", " "), "protected from Push. Merge allowed for Maintainers")

  # Delete main protection if exists
  if (nrow(p_branches) != 0 && "main" %in% p_branches[["name"]]) {
    gitlab(req = paste0("projects/", project_id, "/protected_branches/main"),
           verb = httr::DELETE)
  }

  # Add main protection
  protect_master <- gitlab(req = paste0("projects/", project_id, "/protected_branches"),
                           verb = httr::POST,
                           name = "main",
                           push_access_level = ifelse(isTRUE(unprotect), 40, 0),
                           merge_access_level = 40 # Maintainers
  )
  message("\'main\'", ifelse(isTRUE(unprotect), " not ", " "), "protected from Push. Merge allowed for Maintainers")

  # Delete production protection if exists
  if (nrow(p_branches) != 0 && "production" %in% p_branches[["name"]]) {
    gitlab(req = paste0("projects/", project_id, "/protected_branches/production"),
           verb = httr::DELETE)
  }

  # Add production protection
  protect_prod <- gitlab(req = paste0("projects/", project_id, "/protected_branches"),
                         verb = httr::POST,
                         name = "production",
                         push_access_level = ifelse(isTRUE(unprotect), 40, 0), # 0 = No Ones
                         merge_access_level = 40 # Maintainers
  )
  message("\'production\'", ifelse(isTRUE(unprotect), " not ", " "), " protected from Push and from. Merge allowed for Maintainers")
}
```
  
```{r example-protect_branches, eval=FALSE}
#' \dontrun{
protect_branches(
  project_id = project_id
)
# unprotect if wanted
# protect_branches(project_id, unprotect = TRUE)
#'}
```
  
```{r tests-protect_branches}
test_that("protect_branches works", {

})
```
  
# `modify_autoclose_and_coverage()`: No autoclose issue and coverage regex

```{r function-modify_autoclose_and_coverage}
#' modify_autoclose_and_coverage on GitLab
#'
#' @param project_id project_id
#' @param autoclose Logical. Whether to autoclose issues when merged to main
#' @param build_coverage_regex Character. regex used to retrieve code coverage in Ci logs.
#'
#' @return Side Effect on GitLab
#' @importFrom gitlabr gitlab
#' @export
#'
modify_autoclose_and_coverage <- function(project_id, autoclose = FALSE,
                                          build_coverage_regex = "Coverage: \\d+\\.\\d+") {
  protect_prod <- gitlab(req = paste0("projects/", project_id),
                         verb = httr::PUT,
                         autoclose_referenced_issues = autoclose,
                         build_coverage_regex = build_coverage_regex
  )
  message("Issues are set to", ifelse(autoclose, " ", " not ") ,"auto-close when merged in \'main\'")
  message("build_coverage_regex is set to: ", build_coverage_regex)
}
```
  
```{r example-modify_autoclose_and_coverage, eval=FALSE}
#' \dontrun{
modify_autoclose_and_coverage(
  project_id = project_id
)
#' }
```
  
```{r tests-modify_autoclose_and_coverage}
test_that("modify_autoclose_and_coverage works", {

})
```
  
  
# `project_options()`: Define project status for a user


```{r function-project_options}
#' Define project status for a user
#'
#' @param project_id project_id
#' @param level The notification levels among disabled, participating,
#' watch, global, mention, custom
#' @return Side Effect on GitLab, allow reception of notifications.
#' @export
project_options <- function(project_id, level = "watch") {
  level <- match.arg(level, c("disabled", "participating",
                              "watch", "global", "mention", "custom"))

  protect_notif <- gitlab(req = c("projects", project_id, "notification_settings"),
                         verb = httr::PUT,
                         level = level
  )

  message("Notification setting set for you only: ", protect_notif$level)
}

```
  
```{r example-project_options, eval = FALSE}
#' \dontrun{
project_options(project_id,
                level = "watch")
#' }
```
  
```{r tests-project_options}
test_that("project_options works", {

})
```
  


# Create the board

## `add_labels()`: Add labels

This will add labels "Prêt", "En cours", etc. in your project.


```{r function-add_labels}
#' Add labels to project
#'
#' @param project_id project_id
#' @param lg by default, fr to get labels in french. Use en for english
#'
#' @return Table of added labels. Side effect: labels added on GitLab.
#' @importFrom gitlabr gitlab
#' @importFrom dplyr tribble filter
#' @export
#'
add_labels <- function(project_id, lg = "fr") {
  # Get labels
  labels_already <- gitlab(req = paste0("projects/", project_id, "/labels"),
                           verb = httr::GET)

  # Create missing labels
  if(lg == "fr"){
    labels <- tribble(
      ~name, ~color, ~description,
      "A valider", "#D10069", "Validation client pour mise en ligne",
      "Pr\u00e9-validation", "#F5F5DC", "Validation des tickets par le lead dev avant validation client",
      "Bloqu\u00e9", "#7F8C8D", "N\u00e9cessite des infos compl\u00e9mentaires pour \u00eatre trait\u00e9",
      "En cours", "#428BCA", "En cours de traitement",
      "Pr\u00eat", "#69D100", "Pr\u00eat \u00e0 \u00eatre trait\u00e9",
      # "En attente", "#A8D695", "A ce qu\'il faut pour \u00eatre trait\u00e9e, mais il y a trop de choses dans \'Pr\u00eat\'",
      "R\u00e9vision", "#F0AD4E", "A r\u00e9viser avant int\u00e9gration dans 'main'"
    )
  }else{
    message("English by default")
    labels <- tribble(
      ~name, ~color, ~description,
      "To be validated", "#D10069", "Customer validation to go online",
      "Pre-validation", "#F5F5DC", "Validation of tickets by lead dev before customer validation",
      "Blocked", "#7F8C8D", "Requires additional information to be processed",
      "In progress", "#428BCA", "In progress",
      "Ready", "#69D100", "Pending treatment",
      # "Waiting", "#A8D695", "For what it takes to be treated, but there are too many things in Ready",
      "Review", "#F0AD4E", "To be reviewed before integration into 'main'"
    )
  }
  

  if(nrow(labels_already) !=0){
    labels_to_add <- labels %>%
    filter(!name %in% labels_already$name)
  }else{
    labels_to_add <- labels
  }
  

  if (nrow(labels_to_add) > 0) {
    for (i in 1:nrow(labels_to_add)) {
      gitlab(req = paste0("projects/", project_id, "/labels"),
             verb = httr::POST,
             name = labels_to_add$name[i],
             color = labels_to_add$color[i],
             description = labels_to_add$description[i])
    }
    message("Labels manquants ajout\u00e9s")
  } else {
    message("No new labels to add.")
  }

  labels_to_add
}

```
  
```{r example-add_labels, eval=FALSE}
#' \dontrun{
add_labels(
  project_id = project_id
)
#'}
```
  
```{r tests-add_labels}
test_that("add_labels works", {

})
```
  

## `add_board()`: Create the board

This code prepares the _board_ for the _issues_: Issues > Board > Add List

```{r function-add_board}
#' Add board in the correct order
#'
#' @param project_id project_id
#' @param name Name of the Board
#' @param labels_order Name of the labels already existing in the project
#' @param lg language of the board, "fr" or "en"
#'
#' @importFrom gitlabr gitlab
#' @importFrom tibble tibble
#' @importFrom dplyr left_join filter
#' @export
add_board <- function(
    project_id,
    name = "Development",
    labels_order = c("Bloqu\u00e9", "Pr\u00eat", "En cours", "R\u00e9vision", "Pr\u00e9-validation", "A valider"),
    lg = "fr"
) {

  add_labels(project_id, lg = lg)

  ## Checking if the board already exists
  check_if_board_exists <-
    gitlab(req = paste0("projects/", project_id, "/boards"),
           verb = httr::GET,
           name = name)

  if(nrow(check_if_board_exists) == 0) {

    board <- gitlab(req = paste0("projects/", project_id, "/boards"),
                    verb = httr::POST,
                    name = name)

    message("Created a new board")

  } else {
    
    message("The board already exists")
    
  }

  # get existing list of labels
  all_labels <- gitlab(
    req = c("projects", project_id, "labels"),
    verb = httr::GET)

  # get those for a list in the correct order
  all_labels_lists <- tibble(name = labels_order) %>%
    left_join(all_labels, by = "name") %>%
    filter(!is.na(id))

  # Create lists in the board
  for (label_list in all_labels_lists[["id"]]) {
    gitlab(
      req = c("projects", project_id, "boards", board[["id"]][1], "lists"),
      verb = httr::POST,
      label_id = label_list)
  }

  board <- gitlab(req = paste0("projects/", project_id, "/boards"),
                  verb = httr::GET)

  return(board)
}
```
  
```{r example-add_board, eval = FALSE}
#' \dontrun{
add_board(
  project_id = project_id
)
#'}
```
  
```{r tests-add_board}
test_that("add_board works", {

})
```
  


# Create the Wiki

## `add_wikis()`: Create the wiki pages

This will create some pages in the wiki of your project:

- Home
- Comptes-rendus
- Key dates

```{r function-add_wikis}
#' Add Wiki
#'
#' @param project_id project_id
#' @param project_name project_name
#' @param group_url group_url
#' @param group group
#' @param type type
#'
#' @details
#' Types:
#' - home: Home Page
#' - cr: Comptes-rendus
#' - keys: Key dates of the project
#'
#' @return Tibble with wikis and GitLab infos.
#'
#' @importFrom gitlabr gitlab
#' @export
add_wikis <- function(project_id, project_name, group_url, group = basename(group_url), type = c("home", "cr", "keys")) {

  existing_wiki <- gitlab(req = paste0("projects/", project_id, "/wikis"),
                          verb = httr::GET)

  type <- match.arg(type, several.ok = TRUE)

  if (nrow(existing_wiki) == 0 | "home" %in% type) {
    # Always home
    wiki <- readLines(system.file("gitlab", "wiki_home.md", package = "lozen"))
    # Changer {mon_projet}
    wiki <- gsub(pattern = "\\{mon_projet\\}", replacement = project_name, x = wiki)
    # Changer {group}
    wiki <- gsub(pattern = "\\{group\\}", replacement = group, x = wiki)
    # Changer {url}
    wiki <- gsub(pattern = "\\{url\\}", replacement = group_url, x = wiki)

    # Home
    wiki_home <- gitlab(req = paste0("projects/", project_id, "/wikis"),
                        verb = httr::POST,
                        content = paste(wiki, collapse = "\n"),
                        title = "home",
                        format = "markdown")

    message("Wiki home page added")
  }

  if ("cr" %in% type) {
    # Comptes-rendus
    wiki2 <- readLines(system.file("gitlab", "wiki_cr.md", package = "lozen"))
    # Changer {mon_projet}
    wiki2 <- gsub(pattern = "\\{date\\}", replacement = Sys.Date(), x = wiki2)

    wiki_cr <- gitlab(req = paste0("projects/", project_id, "/wikis"),
                      verb = httr::POST,
                      content = paste(wiki2, collapse = "\n"),
                      title = "Comptes-rendus",
                      format = "markdown")

    message("Wiki Comptes-rendus page added")
  }

  if ("keys" %in% type) {
    # Comptes-rendus
    wiki3 <- readLines(system.file("gitlab", "wiki_keys.md", package = "lozen"))
    # Changer {mon_projet}
    wiki3 <- gsub(pattern = "\\{date\\}", replacement = Sys.Date(), x = wiki3)

    wiki_keys <- gitlab(req = paste0("projects/", project_id, "/wikis"),
                      verb = httr::POST,
                      content = paste(wiki3, collapse = "\n"),
                      title = "Key dates",
                      format = "markdown")

    message("Wiki \'Key dates\' page added")
  }

  gitlab(req = paste0("projects/", project_id, "/wikis"),
         verb = httr::GET)
}

```
  
```{r example-add_wikis, eval=FALSE}
#' \dontrun{
add_wikis(
  project_id = project_id, 
  project_name = project_name, 
  group_url = group_url, 
  group = basename(group_url)
)
}
```
  
```{r tests-add_wikis}
test_that("add_wikis works", {

})
```
  

```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(
  flat_file = "dev/flat_manage_gitlab_projects.Rmd", 
  vignette_name = "bc - Manage GitLab projects",
  overwrite = TRUE,
  check = FALSE, 
  document = FALSE, 
  open_vignette = FALSE
)

rstudioapi::navigateToFile( # Go to the dev_history_package.Rmd to inflate all flat files 
  "dev/dev_history_package.Rmd", 
  line = 170
)
```
