---
title: "flat_init_gitlab_ci.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
library(purrr)
library(yaml)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

## `use_gitlab_ci()`: Set gitlab continuous integration

```{r function-use_gitlab_ci}
# Gitlab-CI
#'
#' Set gitlab continuous integration
#'
#' @param image Docker image used as basis. See \url{https://github.com/rocker-org/rocker}
#' @param project_path Path of the project to add CI in.
#' @inheritParams gitlabr::use_gitlab_ci
#'
#' @details See \code{\link[gitlabr]{use_gitlab_ci}}
#'
#' @export
use_gitlab_ci <- function(
  image = "rocker/verse",
  repo_name = "https://packagemanager.rstudio.com/all/__linux__/focal/latest",
  project_path = ".",
  type = "check-coverage-pkgdown"
    ) {
  ci_file <- file.path(project_path, ".gitlab-ci.yml")
  gitlabr::use_gitlab_ci(
    image = image,
    repo_name = repo_name,
    path = ci_file,
    type = type
  )

  if (grepl("check", type)) {
    lines <- readLines(ci_file)

    install_local <- grep("remotes::install_local\\(upgrade = \"always\"\\)", lines)
    lines[install_local] <- gsub(
      'upgrade = \"always\")',
      'upgrade = \"always\", dependencies = TRUE)',
      lines[install_local]
    )

    script <- grep('"--as-cran"', lines)
    lines[script] <- gsub(',\\s*"--as-cran"', "", lines[script])
    lines[script] <- gsub('"--as-cran"', "", lines[script])

    writeLines(enc2utf8(lines), ci_file)
  }

  if (grepl("pkgdown", type)) {
    lines <- readLines(ci_file)

    stage <- grep("stage: pkgdown$", lines)
    script <- grep("script", lines)
    renv <- grep("renv::restore", lines)

    if (length(renv) == 0) {
      extra <- script[script > stage][1]
    } else {
      renv_extra <- renv[renv > stage][1]
      extra <- script[script > renv_extra][1]
    }
    lines[extra] <- paste0(
      lines[extra],
      "\n",
      # Add extra line
      '    - Rscript -e \'install.packages("thinkrtemplate", repos = c("thinkropen" = "https://thinkr-open.r-universe.dev"))\''
    )

    writeLines(enc2utf8(lines), ci_file)
  }

  ci_file
}
```

```{r examples-use_gitlab_ci, eval = FALSE}
withr::with_tempdir({
  use_gitlab_ci(image = "r-base")
})

withr::with_tempdir({
  use_gitlab_ci(
    image = "rocker/verse",
    repo_name = "https://packagemanager.rstudio.com/all/__linux__/focal/latest",
    type = "check-coverage-pkgdown"
  )
})
```

```{r tests-use_gitlab_ci}
test_that("init_gitlab_ci works for bookdown", {
  # TODO - Remove ; allow test to pass on CI
  skip_on_ci()

  # Test on Gitlab : Create a bookdown and test the CI
  if (Sys.getenv("ALLOW_CI_TESTS_ON_GITLAB", unset = "FALSE") == "TRUE") {
    # Pour un template CI "bookdown"
    output_bookdown <- with_gitlab_project(
      gitlab_url = Sys.getenv("GITLAB_URL", unset = "https://gitlab.com"),
      namespace_id = NULL,
      private_token = Sys.getenv("GITLAB_TOKEN"),
      project_name = "bookdown.test.project",
      exp = {
        bookdown::create_bs4_book(path = ".")
        bookdown::render_book()
        lozen::use_gitlab_ci(type = "bookdown")
      }
    )

    expect_equal(
      object = output_bookdown$status,
      expected = "success"
    )

    # Pour un template CI "bookdown-production"
    # output_bookdown_production <- with_gitlab_project(
    #   gitlab_url = Sys.getenv("GITLAB_URL"),
    #   namespace_id = 1013,
    #   private_token = Sys.getenv("GITLAB_TOKEN"),
    #   project_name = "bookdown.production.test.project",
    #   branch_focus_for_ci = "production",
    #   exp = {
    #     bookdown::create_bs4_book(path = ".")
    #     bookdown::render_book()
    #     lozen::use_gitlab_ci(type = "bookdown-production")
    #   }
    # )
    #
    # expect_equal(object = output_bookdown_production$status,
    #              expected = "success")

    # Test on gitlab.com : Create a bookdown and test the CI
    ## run depending on env variable value
    # TODO
  }
})

test_that("init_gitlab_ci works for shiny", {
  # TODO - Remove ; allow test to pass on CI
  skip_on_ci()

  # Test on Gitlab : Create a Golem and test the CI
  if (Sys.getenv("ALLOW_CI_TESTS_ON_GITLAB", unset = "FALSE") == "TRUE") {
    # Pour un template CI "check-coverage-pkgdown"
    output_golem <- lozen::with_gitlab_project(
      gitlab_url = Sys.getenv("GITLAB_URL", unset = "https://gitlab.com"),
      namespace_id = NULL,
      private_token = Sys.getenv("GITLAB_TOKEN"),
      project_name = "golem.test.project",
      exp = {
        lozen::create_r_project(project_path = getwd(), type = "golem", name_licence = "test", type_licence = usethis::use_mit_license)
        lozen::use_gitlab_ci(type = "check-coverage-pkgdown")
      }
    )

    expect_equal(
      object = output_golem$status,
      expected = "success"
    )
  }
})

test_that("init_gitlab_ci works for a R package", {
  # TODO - Remove ; allow test to pass on CI
  skip_on_ci()

  # Test on Gitlab : Create a Package and test the CI
  if (Sys.getenv("ALLOW_CI_TESTS_ON_GITLAB", unset = "FALSE") == "TRUE") {
    # Pour un template CI "check-coverage-pkgdown"
    output_package <- lozen:::with_gitlab_project(
      gitlab_url = Sys.getenv("GITLAB_URL", unset = "https://gitlab.com"),
      namespace_id = NULL,
      private_token = Sys.getenv("GITLAB_TOKEN"),
      project_name = "package.test.project",
      exp = {
        lozen::create_r_project(project_path = getwd(), type = "package", name_licence = "test", type_licence = usethis::use_mit_license)
        # Add dummy function
        dir.create(file.path(getwd(), "R/"))
        file.create(file.path(getwd(), "R/fun.R"))
        writeLines(con = file.path(getwd(), "R/fun.R"), "somme <- function(a,b) a+b")
        lozen::use_gitlab_ci(type = "check-coverage-pkgdown")
      }
    )

    expect_equal(
      object = output_package$status,
      expected = "success"
    )
  }
})


test_that("init_gitlab_ci works for a quarto or Rmd file", {
  # TODO
})
```


  
## `read_ci()`: Import yaml CI files as list 

Handlers will convert all parameters as list.
    
```{r function-read_ci}
#' read_ci
#'
#' Import yaml CI files as list
#'
#' @param path Path to the yaml file
#'
#' @importFrom yaml read_yaml
#'
#' @return list a list of all CI parameters
#' @export
#'
#' @examples
read_ci <- function(path = "./.gitlab-ci.yml") {
  ci_list <- read_yaml(file = path, handlers = list("seq" = as.list))
  return(ci_list)
}
```
  
```{r example-read_ci}
yaml_path <- system.file("yaml", ".gitlab-ci-shiny.yml", package = "lozen")
ci_list <- read_ci(path = yaml_path)
```
  
```{r tests-read_ci}
test_that("read_ci works", {
  yaml_path <- system.file("yaml", ".gitlab-ci-shiny.yml", package = "lozen")
  ci_list <- read_ci(path = yaml_path)

  expect_equal(
    object = class(x = ci_list),
    expected = "list"
  )
  expect_equal(
    object = ci_list,
    expected = list(
      image = "rocker/verse:latest",
      variables = list(R_LIBS_USER = "ci/lib"),
      cache = list(key = "global-cache", paths = list("${R_LIBS_USER}")),
      stages = list("deploy_connect"),
      deploying = list(
        stage = "deploy_connect",
        script = list(
          "echo \"Library path for packages :\" R_LIBS_USER",
          "mkdir -p R_LIBS_USER",
          "Rscript -e 'install.packages(c(\"git2r\"));install.packages(\"gitlabr\", repos = c(\"https://thinkr-open.r-universe.dev\", \"https://cloud.r-project.org\"))'",
          "Rscript -e 'remotes::install_github(\"thinkr-open/lozen\", build_vignettes = FALSE, ref = Sys.getenv(\"LOZEN_BRANCH\", unset = \"main\"))'",
          "Rscript -e 'lozen::deploy_connect_shiny(connect_url = Sys.getenv(\"CONNECT_URL\"),connect_user = Sys.getenv(\"CONNECT_USER\"),connect_api_token = Sys.getenv(\"CONNECT_TOKEN\"),app_name = Sys.getenv(\"APP_NAME\", unset = Sys.getenv(\"CI_PROJECT_NAME\")))'"
        )
      )
    )
  )
})
```

## `combine_ci()` : Merge two yaml as a list into a combined list
    
```{r function-combine_ci}
#' combine CI
#'
#' Merge two yaml as a list into a combined list
#'
#' @param ci1 List of initial CI parameters
#' @param ci2 List of CI parameters to append to the initial CI
#'
#' @importFrom purrr map map2
#' @importFrom stats setNames
#'
#' @return list list of combined CI parameters
#'
#' @export
combine_ci <- function(ci1, ci2) {
  les_nom <- unique(c(names(ci1), names(ci2)))

  duplicated_with_name <- function(.x, .y, ...) {
    !duplicated(paste(names(.x), .x))
  }

  bonne_base <- les_nom %>%
    map(~ {
      (c(ci1[[.x]], ci2[[.x]]))
    }) %>%
    setNames(les_nom)
  bool <- map2(
    .x = bonne_base,
    .y = names(bonne_base),
    .f = duplicated_with_name
  )
  out <- map2(bonne_base, bool, .f = ~ .x[.y])
  return(out)
}
```
  
```{r example-combine_ci}
# pkgdown yml
full <- yaml::read_yaml(file = system.file("yaml", ".gitlab-ci-pkg.yml", package = "lozen"))

# shiny yaml
connect <- yaml::read_yaml(file = system.file("yaml", ".gitlab-ci-shiny.yml", package = "lozen"))

ci_list <- combine_ci(ci1 = full, ci2 = connect)
```
  
```{r tests-combine_ci}
test_that("combine_ci works", {
  # pkgdown yml
  full <- yaml::read_yaml(file = system.file("yaml", ".gitlab-ci-pkg.yml", package = "lozen"))

  # shiny yaml
  connect <- yaml::read_yaml(file = system.file("yaml", ".gitlab-ci-shiny.yml", package = "lozen"))

  ci_list <- combine_ci(ci1 = full, ci2 = connect)

  expect_equal(
    object = ci_list,
    expected = list(
      image = c("rocker/verse", "rocker/verse:latest"),
      variables = list(
        GIT_DEPTH = 10L,
        REPO_NAME = "https://packagemanager.rstudio.com/all/__linux__/focal/latest",
        R_LIBS_USER = "ci/lib"
      ),
      cache = list(
        key = "global-cache",
        paths = "${R_LIBS_USER}"
      ),
      stages = c(
        "build",
        "test",
        "pkgdown",
        "pkgdown-move",
        "deploy",
        "deploy_connect"
      ),
      building = list(
        stage = "build",
        script = c(
          "lsb_release -c",
          "R -e \"sessionInfo()\"",
          "if [[ $CI_DEFAULT_BRANCH == \"master\" || $CI_DEFAULT_BRANCH = \"main\" ]]; then echo \"OK - Default branch is master or main\"; else echo \"Default branch is not master or main; please add yours ($CI_DEFAULT_BRANCH) where needed, as well as in the present line of code\" ; exit 1; fi",
          "apt-get update -qq && apt-get install -y libharfbuzz-dev libfribidi-dev",
          "echo \"Library path for packages :\" $R_LIBS_USER",
          "mkdir -p $R_LIBS_USER",
          "Rscript -e 'install.packages(\"remotes\")'",
          "Rscript -e 'install.packages(\"rcmdcheck\")'",
          "Rscript -e 'remotes::install_local(upgrade = \"never\")'",
          "R -e 'rcmdcheck::rcmdcheck(args = c(\"--no-manual\"), error_on = \"warning\", check_dir = \"check\")'"
        ),
        artifacts = list(paths = "check", expire_in = "30 days")
      ),
      coverage = list(
        stage = "test",
        allow_failure = TRUE,
        when = "on_success",
        only = c("main", "master", "production"),
        script = c(
          "Rscript -e 'remotes::install_local(upgrade = \"never\")'",
          "Rscript -e 'remotes::install_cran(c(\"covr\", \"DT\"), upgrade = \"never\")'",
          "Rscript -e 'covr::gitlab(quiet = FALSE)'"
        ),
        coverage = "/Coverage: \\d+\\.\\d+/",
        artifacts = list(paths = "public", expire_in = "30 days")
      ),
      integration = list(
        stage = "pkgdown",
        allow_failure = TRUE,
        when = "on_success",
        only = c(
          "main",
          "master",
          "production",
          "test-ci"
        ),
        script = c(
          "Rscript -e 'install.packages(\"thinkrtemplate\", repos = c(\"thinkropen\" = \"https://thinkr-open.r-universe.dev\"))'",
          "Rscript -e 'remotes::install_cran(c(\"pkgdown\"), upgrade = \"never\")'",
          "Rscript -e 'remotes::install_local(upgrade = \"never\")'",
          "Rscript -e 'pkgdown::build_site()'"
        ),
        artifacts = list(
          paths = "docs",
          expire_in = "30 days"
        )
      ),
      `integration-test` = list(
        stage = "pkgdown-move",
        dependencies = "integration",
        only = "test-ci",
        script = c(
          "mkdir -p public/test",
          "curl --location --output artifacts.zip --header \"JOB-TOKEN: $CI_JOB_TOKEN\" \"$CI_API_V4_URL/projects/$CI_PROJECT_ID/jobs/artifacts/$CI_DEFAULT_BRANCH/download?job=pages\" && unzip artifacts.zip && rm artifacts.zip && echo \"copied $CI_DEFAULT_BRANCH artifacts\" || echo \"copied $CI_DEFAULT_BRANCH artifacts failed\"",
          "curl --location --output artifacts.zip --header \"JOB-TOKEN: $CI_JOB_TOKEN\" \"$CI_API_V4_URL/projects/$CI_PROJECT_ID/jobs/artifacts/production/download?job=pages\" && unzip artifacts.zip && rm artifacts.zip && echo \"copied production artifacts\" || echo \"copied production artifacts failed\"",
          "cp -r docs/* public/test"
        ),
        artifacts = list(
          paths = "public",
          expire_in = "30 days"
        )
      ),
      `integration-production` = list(
        stage = "pkgdown-move",
        dependencies = "integration",
        only = "production",
        script = c(
          "mkdir -p public/production",
          "curl --location --output artifacts.zip --header \"JOB-TOKEN: $CI_JOB_TOKEN\" \"$CI_API_V4_URL/projects/$CI_PROJECT_ID/jobs/artifacts/$CI_DEFAULT_BRANCH/download?job=pages\" && unzip artifacts.zip && rm artifacts.zip && echo \"copied $CI_DEFAULT_BRANCH artifacts\" || echo \"copied $CI_DEFAULT_BRANCH artifacts failed\"",
          "cp -r docs/* public/production"
        ),
        artifacts = list(
          paths = "public",
          expire_in = "30 days"
        )
      ),
      `integration-main` = list(
        stage = "pkgdown-move",
        dependencies = "integration",
        only = c("main", "master"),
        script = c(
          "mkdir -p public",
          "curl --location --output artifacts.zip --header \"JOB-TOKEN: $CI_JOB_TOKEN\" \"$CI_API_V4_URL/projects/$CI_PROJECT_ID/jobs/artifacts/production/download?job=pages\" && unzip artifacts.zip && rm artifacts.zip && echo \"copied production artifacts\" || echo \"copied production artifacts failed\"",
          "cp -r docs/* public"
        ),
        artifacts = list(
          paths = "public",
          expire_in = "30 days"
        )
      ),
      pages = list(
        stage = "deploy",
        script = "echo \"deployment with cache\"",
        artifacts = list(
          paths = "public"
        ),
        only = c(
          "main",
          "master",
          "production",
          "test-ci"
        )
      ),
      deploying = list(
        stage = "deploy_connect",
        script = c(
          "echo \"Library path for packages :\" R_LIBS_USER",
          "mkdir -p R_LIBS_USER",
          "Rscript -e 'install.packages(c(\"git2r\"));install.packages(\"gitlabr\", repos = c(\"https://thinkr-open.r-universe.dev\", \"https://cloud.r-project.org\"))'",
          "Rscript -e 'remotes::install_github(\"thinkr-open/lozen\", build_vignettes = FALSE, ref = Sys.getenv(\"LOZEN_BRANCH\", unset = \"main\"))'",
          "Rscript -e 'lozen::deploy_connect_shiny(connect_url = Sys.getenv(\"CONNECT_URL\"),connect_user = Sys.getenv(\"CONNECT_USER\"),connect_api_token = Sys.getenv(\"CONNECT_TOKEN\"),app_name = Sys.getenv(\"APP_NAME\", unset = Sys.getenv(\"CI_PROJECT_NAME\")))'"
        )
      )
    )
  )
})
```

## `clean_image()` : select image in CI info

This function will keep a single docker image from the CI parameters if multiple are in the list. It will keep the image from the initial CI file.

```{r function-clean_image}
#' clean image
#'
#' Manage image in yaml
#'
#' @param ci List of CI parameters, imported from yaml file
#'
#' @return list the list of CI parameters with a unique docker image
#'
#' @export
clean_image <- function(ci) {
  ci[["image"]] <- ci[["image"]][1]
  return(ci)
}
```
  
```{r example-clean_image}
# pkgdown yml
full <- yaml::read_yaml(file = system.file("yaml", ".gitlab-ci-pkg.yml", package = "lozen"))

# shiny yaml
connect <- yaml::read_yaml(file = system.file("yaml", ".gitlab-ci-shiny.yml", package = "lozen"))

ci_list <- combine_ci(ci1 = full, ci2 = connect)
ci_list <- clean_image(ci_list)
```
  
```{r tests-clean_image}
test_that("clean_image works", {
  # pkgdown yml
  full <- yaml::read_yaml(file = system.file("yaml", ".gitlab-ci-pkg.yml", package = "lozen"))

  # shiny yaml
  connect <- yaml::read_yaml(file = system.file("yaml", ".gitlab-ci-shiny.yml", package = "lozen"))

  ci_list_order1 <- clean_image(
    combine_ci(
      ci1 = full,
      ci2 = connect
    )
  )

  expect_equal(
    object = ci_list_order1["image"],
    expected = list(image = "rocker/verse")
  )

  ci_list_order2 <- clean_image(
    combine_ci(
      ci1 = connect,
      ci2 = full
    )
  )

  expect_equal(
    object = ci_list_order2["image"],
    expected = list(image = "rocker/verse:latest")
  )
})
```
  



# check_if_yaml_exists
    
```{r function-check_if_yaml_exists}
#' Check if yaml file exist
#'
#' Check if yaml file already exist and ask permission for overwriting
#'
#'
#'
#' @param dir directory to scan
#' @param file_name filename to use .gitlab-ci.yml
#' @param append boolean do we allow to append stage to existing ci file. TRUE by default
#'
#' @export
check_if_yaml_exists <- function(
  dir = ".",
  file_name = ".gitlab-ci.yml",
  append = TRUE
    ) {
  path_to_yaml <- file.path(dir, file_name)

  if (
    file.exists(path_to_yaml) &&
      !append
  ) {
    append <- utils::askYesNo(
      glue("The file {path_to_yaml} already exists. Do you want to append the  the Connect CI to existing CI stage(s) ?"),
      default = FALSE
    )
  } else {
    append <- TRUE
  }


  # Stop if file exist and append not permitted
  if (
    file.exists(path_to_yaml) &&
      !append
  ) {
    stop(glue("The file {path_to_yaml} already exists. Please remove it or use the argument append = TRUE"))
  }

  return(path_to_yaml)
}
```
  
```{r example-check_if_yaml_exists}
# check_if_yaml_exists()
```
  
```{r tests-check_if_yaml_exists}
test_that("check_if_yaml_exists works", {
  expect_true(inherits(check_if_yaml_exists, "function"))
})
```


# create_deploy_ci_stage
    
```{r function-create_deploy_ci_stage}
#' Title
#'

#' @param image image#'
#' @param deploy_function deploy_function
#' @param stage_name stage_name
#' @param ... dots not used
#' @importFrom purrr map2_chr
#' @importFrom utils getFromNamespace
#' @export
create_deploy_ci_stage <- function(
  image,
  deploy_function,
  stage_name = deploy_function,
  ...
    ) {
  stopifnot("deploy_function exist" = length(getFromNamespace(x = deploy_function, "lozen")) > 0)

  le_call <- glue::glue(
    "Rscript -e 'options(rsconnect.packrat = TRUE); lozen::{deploy_function}(forceUpdate=TRUE, connect_url = Sys.getenv(\"CONNECT_URL\"),connect_user = Sys.getenv(\"CONNECT_USER\"),connect_api_token = Sys.getenv(\"CONNECT_TOKEN\"),app_name = Sys.getenv(\"APP_NAME\", unset = Sys.getenv(\"CI_PROJECT_NAME\")))'"
  )

  # Create list of Connect CI parameters
  connect_ci_list <- list(
    image = image,
    variables = list(
      R_LIBS_USER = "ci/lib"
    ),
    cache = list(
      key = "global-cache",
      paths = list(
        "${R_LIBS_USER}"
      )
    ),
    stages = list(
      stage_name
    ),
    deploying = list(
      stage = stage_name,
      script = c(
        "echo \"Library path for packages :\" $R_LIBS_USER",
        "mkdir -p $R_LIBS_USER",
        # Install git2r and pak
        "Rscript -e 'install.packages(c(\"git2r\"));install.packages(\"gitlabr\", repos = c(\"https://thinkr-open.r-universe.dev\", \"https://cloud.r-project.org\"))'",
        "Rscript -e 'install.packages(\"lozen\", repos = c(\"https://thinkr-open.r-universe.dev\", \"https://cran.rstudio.com\"))'",
        "Rscript -e 'remotes::install_local(dependencies = TRUE)'",
        le_call
      )
    )
  )
  connect_ci_list
}
```
  
```{r example-create_deploy_ci_stage}
create_deploy_ci_stage(
  image = "rocker/verse",
  deploy_function = "deploy_connect_shiny"
)
```
  
```{r tests-create_deploy_ci_stage}
test_that("create_deploy_ci_stage works", {
  expect_true(inherits(create_deploy_ci_stage, "function"))
  expect_true(is.list(create_deploy_ci_stage(
    image = "rocker/verse",
    deploy_function = "deploy_connect_shiny"
  )))
})
```
  
# amend_yaml
    
```{r function-amend_yaml}
#' Amend yaml
#'
#' combien, if needed, to an existing .gitlab-ci.yml file
#'
#'
#' @param path_to_yaml pat to .gtilab-ci.yml file
#' @param connect_ci_list list, output of `create_deploy_ci_stage`
#'
#'
#' @export
amend_yaml <- function(
  path_to_yaml,
  connect_ci_list
    ) {
  # Write CI to yaml
  if (file.exists(path_to_yaml)) {
    # Combine existing and new connect CI if yaml already exist
    init_ci_list <- read_ci(path = path_to_yaml)

    combine_ci(
      ci1 = init_ci_list,
      ci2 = connect_ci_list
    ) |>
      clean_image() |>
      write_yaml(
        file = path_to_yaml,
        line.sep = "\r"
      )
  } else {
    # Write connect CI as yaml if no yaml currently exist
    connect_ci_list |>
      write_yaml(
        file = path_to_yaml,
        line.sep = "\r"
      )
  }
}
```
  
```{r example-amend_yaml}
# amend_yaml()
```
  
```{r tests-amend_yaml}
test_that("amend_yaml works", {
  expect_true(inherits(amend_yaml, "function"))
})
```
  
# Inflate  
  
  
```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(
  flat_file = "dev/flat_init_gitlab_ci.Rmd",
  vignette_name = "be - Initilialise GitLab CI",
  overwrite = TRUE,
  check = FALSE,
  document = TRUE,
  open_vignette = FALSE
)

rstudioapi::navigateToFile(
  # Go to the dev_history_package.Rmd to inflate all flat files
  "dev/dev_history_package.Rmd",
  line = 173
)
```
