---
title: "Create a new projet with GitLab"
output: html_document
editor_options: 
  chunk_output_type: console
---

*This flat file is only used to generate a vignette that explains how to initiate a new project with Gitlab*. If you need to modify the functions or the unit tests, please go to the dedicated flat file. 

The possible products are the following ones:

- An R package, versioned, continuously integrated and whose pkgdown is continuously deployed on Connect
- A Shiny app ({golem}), versioned, continuously integrated and whose pkgdown and the corresponding app are continuously deployed on Connect
- A bookdown, versioned, continuously integrated and continuously deployed on Connect

The following instructions are used to initiate a product on your Forge. But they can be adapted to initiate a product on GitLab.com, by changing the `gitlab_url` and the `private_token` where needed.

# Packages

```{r, include = FALSE}
library(gitlabr)
library(lozen)
library(dplyr)
```

# Define the name of the principal branch

```{bash}
git config --global init.defaultBranch main
```

# Connection to GitLab

- Create environment variable `GITLAB_TOKEN` with api token on gitlab.com or your own gitlab
  + Store it in `".Renviron"` with `usethis::edit_r_environ()`

```{r, eval=FALSE}
gitlab_url <- Sys.getenv("GITLAB_URL", unset = "https://gitlab.com")

# GitLab con
my_gitlab <- gl_connection(
  gitlab_url = gitlab_url,
  private_token = Sys.getenv("GITLAB_TOKEN")
)

# Set the connection for the session
set_gitlab_connection(my_gitlab)
```

# Create a new project or use an existing project

Here, you will have to choose if: 

- You want to create a new project 
- You wan to use an existing project, previously created on Forge

Go to the dedicated subsection below.

## Create a new project

### Get groups

You must define in which group you want to create your project. 

Replace the value `"my_group"` by the name of the group.

The `namespace_id` of the group you want to use will be used in the next steps.

```{r, eval=FALSE}
# Get user namespace (= group_id)
namespace_id <- gitlabr::gitlab(req = "namespaces", search = "my_group")[["id"]]
# If you are not working within a group, please set it to NULL
namespace_id <- NULL
```

### Create the new project

Define:

- The name of the project you want to create in `project_name` *(Choose it as for package name. No special character, only dot if needed)*
- The `namespace_id` of the group where you want to create your project

```{r, eval=FALSE}
project_name <- "myrandomproject"
```

Create the new project:

```{r, eval=FALSE}
project_id <- create_group_project(
  project_name = project_name,
  namespace_id = namespace_id,
  default_branch = "main"
)
```

## Use an existing project

Define:

- The `project_id` of the project you want to use

```{r, eval=FALSE}
project_id <- 123456789
```

# Get all information about the project

```{r, eval=FALSE}
the_project <- gl_get_project(
  project = project_id
)

project_name <- the_project[["name"]]
group_url <- gsub(the_project[["name"]], "", the_project[["web_url"]])
```

# Clone your project and add the skeleton for your product (package, app, bookdown)

You will be able to create the first skeleton of your product, depending if it is a package, a Shiny app, etc.

## Define local installation and clone

This code will clone the GitLab project locally, in a temporary directory.

```{r, eval=FALSE}
project_path <- clone_locally(
  project_name = the_project[["name"]],
  group_url = group_url,
  open = FALSE
)
```

## Create the skeleton for your product and initiate the CI/CD

### R package skeleton

#### Create a basic R package

```{r, eval=FALSE}
create_r_project(
  project_path = project_path,
  type = "package",
  name_licence = "example",
  type_licence = usethis::use_mit_license
)
```

#### Initiate the CI/CD

```{r, eval=FALSE}
lozen::use_gitlab_ci(
  project_path = project_path,
  type = "check-coverage-pkgdown"
)
```

Please note that the `R/` and `tests/` folders will be missing from the R package created using `create_r_project(type = "package")`. If these folders remains missing, the "coverage" job of the "test" stage of the CI pipeline will fail (the following steps of the CI pipeline will nevertheless be run). 

### Shiny app

#### Create a basic {golem} shiny app

```{r, eval=FALSE}
create_r_project(
  project_path = project_path,
  type = "golem",
  name_licence = "Name licence",
  type_licence = usethis::use_proprietary_license
)
```

#### Initiate the CI/CD

```{r, eval=FALSE}
lozen::use_gitlab_ci(
  project_path = project_path,
  type = "check-coverage-pkgdown"
)
```

### Bookdown

#### Create a basic bookdown

```{r, eval=FALSE}
bookdown::create_bs4_book(
  path = project_path
)
```

#### Initiate the CI/CD

```{r, eval=FALSE}
lozen::use_gitlab_ci(
  project_path = project_path,
  type = "bookdown"
)
```

## Create weekly

```{r, eval=FALSE}
# The file to create weekly
file.copy(
  from = system.file("doc", "ac-create-weekly-with-github-or-gitlab.Rmd",
    package = "lozen"
  ),
  to = file.path(
    project_path, "dev",
    "lead_dev_create_weekly.Rmd"
  )
)
```

## Manage a calendar

Use your tools or vignette to manage your calendar for this project.

## Add commit templates

```{r, eval=FALSE}
add_git_templates(
  project_path = project_path,
  type = c("commit", "mr")
)
```

> Tell all devs to run this in their own project `gert::git_config_set(repo = project_path, name = "commit.template", value = ".gitlab/template_commit")`

## Add issues templates

2 templates will be added for the issues that will be opened on your project: 

- A "light" template
- A "full" template that contains all the information required to complete the issues

```{r, eval=FALSE}
gl_add_template_issue(
  project_path = project_path,
  language = "fr" # you can use "en" instead
)
```

## Push to server

```{r, eval=FALSE}
push_main(
  project_path = project_path
)
```

## Create a _production_ branch

```{r, eval=FALSE}
create_production(
  project_path = project_path
)
```

## Protect branches

```{r, eval=FALSE}
protect_branches(
  project_id = project_id
)
```

# No autoclose issue and coverage regex

```{r, eval=FALSE}
modify_autoclose_and_coverage(
  project_id = project_id
)
```

# Create the board on Forge

## Add labels

This will add labels "Prêt", "En cours", etc. in your project.

```{r, eval=FALSE}
add_labels(
  project_id = project_id
)
```

## Create the board

This code prepares the _board_ for the _issues_: Issues > Board > Add List

+ If the labels are duplicated, go to Issues > Labels. Delete all the "project labels" by clicking on the 3 vertical dots, then Delete. The list of labels is now empty, but if you go back to the _board_, you will still have the global labels available, in one copy.

```{r, eval=FALSE}
add_board(
  project_id = project_id
)
```

## Add some special issues in the board

### Add the first issue for the client

```{r, eval=FALSE}
add_issue_clients(
  project_id = project_id,
  project_name = project_name,
  group_url = group_url
)
```

### Add the issue that will be shown during the kick-off

```{r, eval=FALSE}
add_issue_kickoff(
  project_id = project_id
)
```

### Add the todo for the Lead Dev

```{r, eval=FALSE}
add_issue_dev(
  project_id = project_id,
  group_url = group_url,
  project_name = project_name
)
```

# Create the wiki pages

This will create some pages in the wiki of your project:

- Home
- Comptes-rendus
- Key dates

```{r, eval=FALSE}
add_wikis(
  project_id = project_id,
  project_name = project_name,
  group_url = group_url,
  group = basename(group_url)
)
```

```{r tests-create_new_project_gitlab, filename = "create_new_project_gitlab"}
library(gitlabr)
library(dplyr)

skip_on_ci()
skip_if_offline()

gitlab_url <- Sys.getenv("GITLAB_URL", unset = "https://gitlab.com")

the_token <- Sys.getenv("GITLAB_TOKEN")

options(
  remotes.git_credentials =
    git2r::cred_user_pass("gitlab-ci-token", the_token)
)

# GitLab con
my_gitlab <- gl_connection(
  gitlab_url = gitlab_url,
  private_token = the_token
)

# Set the connection for the session
set_gitlab_connection(my_gitlab)

# Get user infos
user_info <- gitlab(req = paste0("user"), verb = httr::GET)
user_name <- user_info %>% pull(username)

project_name <- paste0("lozenprojectforunittest")

# Get user namespace (= group_id)
# namespace_id <- gitlabr::gitlab(req = "namespaces", search = user_name)[["id"]]
group_url <- user_info[["web_url"]]


# create_group_project ----
test_that("create_group_project works", {
  expect_message(create_group_project(project_name, namespace_id = NULL))
})

expect_message(project_id <- create_group_project(project_name, namespace_id = NULL, default_branch = "main"),
  regexp = "already exists"
)

# add_labels ----
test_that("add_labels works", {

  ## Add new
  add_labels(project_id)

  ## Add again but nothing append
  expect_message(labels <- add_labels(project_id), "No new labels to add")
  
  expect_equal(nrow(labels), 0)
  
})

# add_board ----
test_that("add_board works", {
  board <- add_board(project_id)

  expect_equal(nrow(board), 1)
})

# add_issue_clients ----
test_that("add_issue_clients works", {
  expect_message(issue <- add_issue_clients(project_id, project_name, group_url), "Issue Client")
  expect_equal(issue[["iid"]], "1")
})

# add_wikis ----
test_that("add_wikis works", {
  expect_message(
    wiki <- add_wikis(project_id, project_name, group_url, group = basename(group_url)),
    "Wiki home"
  )
  expect_equal(nrow(wiki), 3)
})

# clone_locally ----
test_that("clone_locally works", {
  expect_message(
    clone <- clone_locally(project_name, group_url, open = FALSE)
  )
  expect_true(dir.exists(clone))
  expect_true(dir.exists(file.path(clone, ".git")))
  # expect_equal(clone, project_path)
  unlink(clone, recursive = TRUE)
})

expect_error(
  project_path <- clone_locally(project_name, group_url, open = FALSE),
  regexp = NA
)

expect_message(
  r_project <- create_r_project(project_path, type = c("package"), name_licence = "test", type_licence = usethis::use_mit_license),
  "package created"
)

# push_main ----
test_that("push_main works", {
  expect_message(push_main(project_path))
  # Verify on GitLab
  branches <- gitlabr::gl_list_branches(project_id)
  expect_true(branches[["name"]] %in% c("main", "master"))
})

# create_production ----
test_that("create_production works", {
  expect_message(create_production(project_path))
  branche <- gitlabr::gl_get_branch(project_id, "production")
  expect_true(nrow(branche) > 0)
})

# protect_branches ----
test_that("protect_branches works", {
  expect_message(protect_branches(project_id))
  p_branches <- gitlab(
    req = paste0("projects/", project_id, "/protected_branches"),
    verb = httr::GET
  )
  expect_equal(p_branches[["push_access_levels.access_level"]], c("0", "0", "0"))
})

# modify_autoclose_and_coverage ----
test_that("modify_autoclose_and_coverage works", {
  expect_message(modify_autoclose_and_coverage(project_id))
})

# Modify project_options ----
test_that("project_options works", {
  expect_message(project_options(project_id), "Notification setting set for you only: watch")
})

# add_issue_dev ----
test_that("add_issue_dev works", {
  expect_message(add_issue_dev(project_id, group_url, project_name))
  issues_list <- gl_list_issues(project = project_id)
  expect_true(any(grepl("Checklist", issues_list[["title"]])))
})

# Clean
unlink(project_path, recursive = TRUE)

# Clean GitLab => Remove the project
gitlab(
  req = paste0("projects/", project_id),
  verb = httr::DELETE
)
```





```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(
  flat_file = "dev/flat_create_new_project_gitlab.Rmd",
  vignette_name = "aa - Create a new project with GitLab",
  overwrite = TRUE,
  check = FALSE,
  document = FALSE,
  open_vignette = FALSE
)

rstudioapi::navigateToFile( # Go to the dev_history_package.Rmd to inflate all flat files
  "dev/dev_history_package.Rmd",
  line = 170
)
```

