---
title: "Create the skeleton of the R project (package, app, book)"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

# `create_r_project()`: Create a R project with full content skeleton

```{r function-create_r_project}
#' Create a R project with full content skeleton
#'
#' @param project_path project_path
#' @param type type
#' @param name_licence name for the licence
#' @param type_licence type of the licence, should be a function like usethis::use_mit_licence
#'
#' @return Side Effect: Transform project as package or book:
#'
#' - With package, golem or book skeleton
#' - git necessary files
#' - pkgdown or book template
#' - GitLab CI
#'
#' @export
#'
create_r_project <- function(project_path, type = c("package", "golem", "book"), name_licence, type_licence) {
  type <- match.arg(type)

  if (type == "book") {
    create_book_project(project_path)
  } else {
    # Transform as R package
    # Change wd and proj for usethis
    # old <- setwd(project_path)
    # Create project in case not already a project
    usethis::create_project(project_path, open = FALSE)
    # create content
    usethis::with_project(project_path, {
      if (type == "package") {
        usethis::create_package(path = project_path, open = FALSE)
        attachment::att_amend_desc()
      } else if (type == "golem") {
        golem::create_golem(path = project_path, open = FALSE, overwrite = TRUE)
        attachment::att_amend_desc()
      }
    })
  }
  # setwd(old)

  add_kit_project(project_path, name_licence = name_licence, type_licence = type_licence)

  if (type %in% c("package", "golem")) {
    add_kit_package(project_path)
  }

  project_path
}
```

```{r example-create_r_project, eval=FALSE}
### R package skeleton
withr::with_tempdir({
  project_path <- getwd()
  create_r_project(
    project_path,
    type = c("package"),
    name_licence = "Bob",
    type_licence = usethis::use_proprietary_license
  )
})


### Shiny app
withr::with_tempdir({
  project_path <- getwd()
  create_r_project(
    project_path,
    type = c("golem"),
    name_licence = "Bob",
    type_licence = usethis::use_proprietary_license
  )
})

### Bookdown
withr::with_tempdir({
  project_path <- getwd()
  create_r_project(
    project_path,
    type = c("book"),
    name_licence = "Bob",
    type_licence = usethis::use_proprietary_license
  )
})

```


```{r tests-create_r_project}
test_that("create_r_project works", {

})
```

# Transform project as book with lozen template with `create_book_project()`

```{r function-create_book_project, filename = "create_book_project"}
#' Transform project as book with lozen template
#'
#' @param project_path project_path
#' @param bookdown_path a path to a bookdown
#' @param css path(s) for css to copy
#' @param footer path for footer to copy
#' @param logo path for logo to copy
#' @param index path for index to copy
#' @param output_yml path for output_yml to copy

#'
#' @return Side Effect: Transform project as book
#' @export
create_book_project <- function(project_path,
                                bookdown_path = system.file("lozendown", package = "lozen"),
                                css = NULL,
                                footer = NULL,
                                logo = NULL,
                                index = NULL,
                                output_yml = NULL) {
  old <- setwd(project_path)
  on.exit(setwd(old))

  all_files <- list.files(
    bookdown_path,
    full.names = TRUE,
    all.files = TRUE,
    no.. = TRUE
  )


  alldirs <- all_files[fs::is_dir(all_files)]
  purrr::walk(alldirs, ~ fs::dir_copy(.x, project_path))
  allfiles <- all_files[!fs::is_dir(all_files)]
  purrr::walk(allfiles, ~ fs::file_copy(.x, project_path))

  ## Add dev_history_book in "dev/"
  dev_path <- file.path(project_path, "dev")
  if (!file.exists(dev_path)) {
    dir.create(path = dev_path)
  }
  use_dev_history(path = project_path, type = c("book", "renv"))

  # ## Template HTML
  ## CSS
  if (!is.null(css)) {
    file.copy(from = css, to = project_path, overwrite = TRUE)
  }
  ## FOOTER
  if (!is.null(footer)) {
    file.copy(from = footer, to = project_path, overwrite = TRUE)
  }
  ## logo
  if (!is.null(logo)) {
    file.copy(from = logo, to = project_path, overwrite = TRUE)
  }

  # ## Modify index.Rmd
  if (!is.null(index)) {
    file.copy(
      index,
      "index.Rmd",
      overwrite = TRUE
    )
  }

  ## DESCRIPTION
  file_desc <- file.path(project_path, "DESCRIPTION")
  if (!file.exists(file_desc)) {
    fields <- c(list(Type = "Compendium"), usethis::use_description_defaults())
    desc <- desc::desc(text = glue::glue("{names(fields)}: {fields}"))
    desc$write(file_desc)
  }
  # Update content
  imports <- unique(c("bookdown", "knitr", attachment::att_from_rmds(".", recursive = FALSE)))
  attachment::att_to_desc_from_is(path.d = file_desc, imports = imports)

  ## Add _output.yml pour template lozen
  if (!is.null(output_yml)) {
    file.copy(
      output_yml,
      file.path(project_path, "_output.yml"),
      overwrite = TRUE
    )
  }

  ## Hide _book from git
  # gitignore
  add_git_ignore(c(
    "_book/", "*.log", "_main.tex", "*_files/", ".Rproj.user",
    ".Rhistory", "gitbook.*"
  ))

  message("book created")
  message("You need to follow \'dev_history_book.Rmd\' after that for the CI to create the pdf_book.")
  project_path
}
```

```{r example-create_book_project, eval=FALSE}
withr::with_tempdir({
  project_path <- getwd()
  create_book_project(project_path)
})
```

```{r tests-create_book_project}
# test_that("create_book_project works", {
#
# })
```


# `add_kit_project()`: Add necessary files for any R project

```{r function-add_kit_project}
#' Add necessary files for any R project
#'
#' @param project_path project_path
#' @param name_licence Name for the licence
#' @param type_licence should be a function, example : type_licence = usethis::use_proprietary_license
#'
#' @return Side Effect, add new files :
#'
#' - gitattributes
#' - NEWS.md
#'
#' @export
#'
add_kit_project <- function(project_path = ".", name_licence, type_licence) {
  if (!inherits(type_licence, "function")) {
    stop("type_licence should be a function, example : type_licence = usethis::use_proprietary_license")
  }
  # Add gitattributes
  gitattributes <- system.file("gitlab", "gitattributes", package = "lozen")
  file.copy(gitattributes, file.path(project_path, ".gitattributes"), overwrite = TRUE)

  # Change wd and proj for usethis
  # old <- setwd(project_path)
  # on.exit(setwd(old))
  usethis::with_project(project_path, setwd = TRUE, {
    # Licence
    type_licence(name_licence)

    # NEWS
    usethis::use_template("NEWS.md", data = list(), open = FALSE)
  })

  message("Kit project created")
}
```

```{r example-add_kit_project, eval=FALSE}
withr::with_tempdir({
  project_path <- getwd()
  usethis::create_project(path = project_path, open = FALSE)
  add_kit_project(
    project_path,
    name_licence = "Bob",
    type_licence = usethis::use_proprietary_license
  )
})
```

```{r tests-add_kit_project}
# test_that("add_kit_project works", {
#
# })
```

# `add_kit_package()`: Add files necessary for a package, including {golem}

```{r function-add_kit_package}
#' Add files necessary for a package, including {golem}
#'
#' @param project_path project_path
#' @param pkgdown_yml path to yaml conf for pkgdown
#' @inheritParams use_dev_history
#'
#' @return Side Effect, add new files :
#'
#' - dev/dev_history
#' - templates for pkgdown if pkgodwn_yml is not null
#' - testthat
#'
#' @export
#'
add_kit_package <- function(project_path = ".",
                            type = c("package", "renv"),
                            pkgdown_yml = NULL) {
  type <- match.arg(type, several.ok = TRUE)

  ## Add dev_history in "dev/"
  dev_path <- normalizePath(file.path(project_path, "dev"), mustWork = FALSE)
  if (!dir.exists(dev_path)) {
    dir.create(dev_path)
  }
  use_dev_history(path = project_path, type = type)

  ## Add pkgdown file
  old <- setwd(project_path)
  on.exit(setwd(old))
  usethis::with_project(project_path, setwd = TRUE, {
    # gitignore
    add_git_ignore(c("docs"))
    # buildignore
    add_build_ignore(c("_pkgdown.yml", "pkgdown", "ci/lib"))

    if (!is.null(pkgdown_yml)) {
      file.copy(
        pkgdown_yml,
        file.path(project_path, "_pkgdown.yml")
      )
    }


    ## Add testthat
    usethis::use_testthat()
    usethis::use_test("start")
  })
  message("Kit package created")

  return(project_path)
}
```

```{r example-add_kit_package, eval=FALSE}
withr::with_tempdir({
  project_path <- getwd()
  usethis::create_package(path = project_path, open = FALSE)
  add_kit_package(project_path, type = c("package", "book", "renv"))
})
```

```{r tests-add_kit_package}
test_that("add_kit_package works", {

})
```

# Add files to buildignore : `add_build_ignore()`

```{r function-add_build_ignore}
#' Add files to Rbuildignore
#'
#' @param x vector of filenames
#' @param directory path where to Rbuildignore should be written
add_build_ignore <- function(x, directory = ".") {
  build_file <- file.path(directory, ".Rbuildignore")

  if (!file.exists(build_file)) {
    writeLines("", build_file)
  }

  build_ignore <- readLines(build_file)

  to_ignore <- paste0("^", gsub("[.]", "\\\\.", x), "$")

  to_ignore <- to_ignore[!to_ignore %in% build_ignore]

  if (length(to_ignore) != 0) {
    writeLines(enc2utf8(c(build_ignore, to_ignore)), build_file)
  }
}
```

```{r example-add_build_ignore, eval=FALSE}
withr::with_tempdir({
  add_build_ignore("rsconnect/", directory = ".")
})
```

```{r tests-add_build_ignore}
test_that("add_build_ignore works", {

})
```

# Add files to gitignore : `add_git_ignore()`

```{r function-add_git_ignore}
#' Add files to gitignore
#'
#' @param x vector of filenames
#' @param directory path where to .gitignore should be written
add_git_ignore <- function(x, directory = ".") {
  git_file <- file.path(directory, ".gitignore")

  if (!file.exists(git_file)) {
    writeLines("", git_file)
  }

  git_ignore <- readLines(git_file)

  to_ignore <- x

  to_ignore <- x[!x %in% git_ignore]

  if (length(to_ignore) != 0) {
    writeLines(enc2utf8(c(git_ignore, to_ignore)), git_file)
  }
}
```

```{r example-add_git_ignore, eval=FALSE}
withr::with_tempdir({
  add_git_ignore("*.R", directory = ".")
})
```

```{r tests-add_git_ignore}
test_that("add_git_ignore works", {

})
```

# Use a dev history file

`use_dev_history()` creates `dev_history.Rmd` files:

- "dev_history_package": Instructions to create and develop a R package
- "dev_history_renv": Instructions to init renv

This function will put the file into your "dev" folder.

```{r function-use_dev_history}
#' Une a dev histroy file
#'
#' @param path Path to project to add dev_history in
#' @param type Type of dev_history. Multiple types possible among "package", "book", "renv".
#'
#' @export
use_dev_history <- function(path = ".", type = c("package", "renv")) {
  type <- match.arg(type, choices = c("package", "book", "renv"), several.ok = TRUE)

  old <- setwd(path)
  on.exit(setwd(old))

  if (!dir.exists(file.path(path, "dev"))) {
    dir.create(file.path(path, "dev"))
  }

  if (any(grepl("connect", type))) {
    add_git_ignore("rsconnect/", directory = path)
  }

  for (i in type) {
    file <- system.file("package", paste0("dev_history_", i, ".R"), package = "lozen")
    if (file == "") {
      file <- system.file("package", paste0("dev_history_", i, ".Rmd"), package = "lozen")
    }
    if (file == "") {
      file <- system.file("package", paste0("flat_", i, ".Rmd"), package = "lozen")
    }
    if (file == "") {
      stop("template ", i, " not found")
    }
    file.copy(file, file.path(path, "dev"))
  }

  add_build_ignore("dev")
}
```

```{r examples-use_dev_history, eval=FALSE}
withr::with_tempdir({
  use_dev_history(path = ".", type = c("package", "book", "renv"))
})
```

```{r tests-use_dev_history}
test_that("use_dev_history works", {

})
```


```{r tests-local_project, filename = "local_project"}
project_path <- tempfile("my.project")
dir.create(project_path)
# usethis::create_project(project_path, open = FALSE)

# create_r_project ----
test_that("create_r_project works", {
  # project_path <- usethis::create_project(path = tempfile(), open = FALSE)
  expect_message(
    r_project <- create_r_project(project_path, type = c("package"), name_licence = "Test", type_licence = usethis::use_mit_license),
    "package created"
  )
  # expect_equal(r_project, project_path)
  expect_true(file.exists(file.path(r_project, "DESCRIPTION")))
  expect_true(file.exists(file.path(r_project, "NAMESPACE")))
  # expect_true(file.exists(file.path(r_project, "_pkgdown.yml")))
  expect_true(file.exists(file.path(r_project, ".gitattributes")))
  expect_true(file.exists(file.path(r_project, "dev", "dev_history_package.Rmd")))
  expect_true(file.exists(file.path(r_project, "dev", "dev_history_renv.Rmd")))
  expect_true(file.exists(file.path(r_project, "NEWS.md")))
  expect_true(file.exists(file.path(r_project, "LICENSE")))
})

# add_git_templates ----
test_that("add_git_templates works", {
  # project_path is not a git repository in this case
  expect_message(
    add_git_templates(project_path, type = c("commit")),
    "this is not a git repository"
  )
  expect_true(file.exists(file.path(project_path, ".gitlab", "template_commit")))
  expect_message(
    add_git_templates(project_path, type = c("mr")),
    "MR template added"
  )
  expect_true(file.exists(file.path(project_path, ".gitlab", "merge_request_templates", "template_mr.md")))

  # project_path is a git repository in this case
  gert::git_init(project_path)
  expect_message(
    add_git_templates(project_path, type = c("commit")),
    "Your local git configuration"
  )
})

# Clean local projects
unlink(project_path, recursive = TRUE)

# BOOK ====
project_path_book <- tempfile("book-")
dir.create(project_path_book)

# create_book_project ----
test_that("create_book_project works", {
  expect_message(
    r_project <- create_book_project(project_path_book),
    "book created"
  )
  expect_equal(r_project, project_path_book)
  # (!file.exists(file.path(project_path_book, "DESCRIPTION")))
  expect_true(file.exists(file.path(project_path_book, "DESCRIPTION")))

  expect_true(file.exists(file.path(r_project, "dev", "dev_history_book.Rmd")))
  expect_true(file.exists(file.path(r_project, "R", "functions_exemples.R")))
  expect_true(file.exists(file.path(r_project, "pandoc", "reference.odt")))
  # expect_true(file.exists(file.path(r_project, ".gitlab-ci.yml")))
  # expect_true(file.exists(file.path(r_project, ".gitattributes")))
  expect_true(file.exists(file.path(r_project, ".gitignore")))
  expect_true(all(
    file.exists(
      file.path(
        r_project,
        c(
          "01-page1.Rmd", "02-page2.Rmd", "03-page3.Rmd",
          "DESCRIPTION", "_bookdown.yml"
        )
      )
    )
  ))
})

# add_kit_project to book ----
add_kit_project(project_path = project_path_book, name_licence = "Test", type_licence = usethis::use_mit_license)
test_that("add_kit_project works", {
  expect_true(file.exists(file.path(project_path_book, ".gitattributes")))
  expect_true(file.exists(file.path(project_path_book, "NEWS.md")))
  expect_true(file.exists(file.path(project_path_book, "LICENSE")))
})

# Clean local projects
unlink(project_path_book, recursive = TRUE)
```




```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(
  flat_file = "dev/flat_create_r_project_skeleton.Rmd",
  vignette_name = "ac - Create the skeleton of the R project (package, app, book)",
  overwrite = TRUE,
  check = FALSE,
  document = TRUE,
  open_vignette = FALSE
)

rstudioapi::navigateToFile( # Go to the dev_history_package.Rmd to inflate all flat files
  "dev/dev_history_package.Rmd",
  line = 170
)
```

