---
title: "Create a new projet with GitLab"
output: html_document
editor_options: 
  chunk_output_type: console
---

*This flat file is only used to generate a vignette that explains how to initiate a new project with Gitlab*. If you need to modify the functions or the unit tests, please go to the dedicated flat file. 

The possible products are the following ones:

- An R package, versioned, continuously integrated and whose pkgdown is continuously deployed on Connect
- A Shiny app ({golem}), versioned, continuously integrated and whose pkgdown and the corresponding app are continuously deployed on Connect
- A bookdown, versioned, continuously integrated and continuously deployed on Connect

The following instructions are used to initiate a product on your Forge. But they can be adapted to initiate a product on GitLab.com, by changing the `gitlab_url` and the `private_token` where needed.

# Packages

```{r, include = FALSE}
library(gitlabr)
library(lozen)
library(dplyr)
```

# Define the name of the principal branch

```{bash}
git config --global init.defaultBranch main
```

# Connection to GitLab

- Create environment variable `GITLAB_TOKEN` with api token on gitlab.com or your own gitlab
  + Store it in `".Renviron"` with `usethis::edit_r_environ()`

```{r, eval=FALSE}
gitlab_url <- Sys.getenv("GITLAB_URL", unset = "https://gitlab.com")

# GitLab con
my_gitlab <- gl_connection(
  gitlab_url = gitlab_url,
  private_token = Sys.getenv("GITLAB_TOKEN")
)

# Set the connection for the session
set_gitlab_connection(my_gitlab)
```

# Create a new project or use an existing project

Here, you will have to choose if: 

- You want to create a new project 
- You wan to use an existing project, previously created on Forge

Go to the dedicated subsection below.

## Create a new project

### Get groups

You must define in which group you want to create your project. 

Replace the value `"my_group"` by the name of the group.

The `namespace_id` of the group you want to use will be used in the next steps.

```{r, eval=FALSE}
# Get user namespace (= group_id)
namespace_id <- gitlabr::gitlab(req = "namespaces", search = "my_group")[["id"]]
# If you are not working within a group, please set it to NULL
namespace_id <- NULL
```

### Create the new project

Define:

- The name of the project you want to create in `project_name` *(Choose it as for package name. No special character, only dot if needed)*
- The `namespace_id` of the group where you want to create your project

```{r, eval=FALSE}
project_name <- "myrandomproject"
```

Create the new project:

```{r, eval=FALSE}
project_id <- create_group_project(
  project_name = project_name,
  namespace_id = namespace_id,
  default_branch = "main"
)
```

## Use an existing project

Define:

- The `project_id` of the project you want to use

```{r, eval=FALSE}
project_id <- 123456789
```

# Get all information about the project

```{r, eval=FALSE}
the_project <- gl_get_project(
  project = project_id
)

project_name <- the_project[["name"]]
group_url <- gsub(the_project[["name"]], "", the_project[["web_url"]])
```

# Clone your project and add the skeleton for your product (package, app, bookdown)

You will be able to create the first skeleton of your product, depending if it is a package, a Shiny app, etc.

## Define local installation and clone

This code will clone the GitLab project locally, in a temporary directory.

```{r, eval=FALSE}
project_path <- clone_locally(
  project_name = the_project[["name"]],
  group_url = group_url,
  open = FALSE
)
```

## Create the skeleton for your product and initiate the CI/CD
   
To initiate a new product, please take a look at the following vignette : `vignettes/ac-create-the-skeleton-of-the-r-project--package-app-book-.Rmd`.

## Initiate the CI/CD

To set up continuous integration and continuous deployment of your product, please take a look at the following vignette : `vignettes/ad-set-up-continuous-integration-and-deployment-through-gitlab-ci.Rmd`.


# Manage git tools (branches, commits, issues, etc.)

Please take a look at the following vignette : `vignettes/bb-manage-git-tools--branches-commits-etc--.Rmd`.


# Create and manage the forge board and wiki

Please take a look at the following vignette : `vignettes/ba-manage-forge-board-wiki.Rmd`.


# Visualise the status of your project

Please take a look at the following vignette : `ae-create-weekly-with-github-or-gitlab.Rmd`.

<!-- # Units tests -->
```{r tests-create_new_project_gitlab, filename = "create_new_project_gitlab"}
library(gitlabr)
library(dplyr)

skip_on_ci()
skip_if_offline()

gitlab_url <- Sys.getenv("GITLAB_URL", unset = "https://gitlab.com")

the_token <- Sys.getenv("GITLAB_TOKEN")

options(
  remotes.git_credentials =
    git2r::cred_user_pass("gitlab-ci-token", the_token)
)

# GitLab con
my_gitlab <- gl_connection(
  gitlab_url = gitlab_url,
  private_token = the_token
)

# Set the connection for the session
set_gitlab_connection(my_gitlab)

# Get user infos
user_info <- gitlab(req = paste0("user"), verb = httr::GET)
user_name <- user_info %>% pull(username)

project_name <- paste0("lozenprojectforunittest")

# Get user namespace (= group_id)
# namespace_id <- gitlabr::gitlab(req = "namespaces", search = user_name)[["id"]]
group_url <- user_info[["web_url"]]


# create_group_project ----
test_that("create_group_project works", {
  expect_message(create_group_project(project_name, namespace_id = NULL))
})

expect_message(project_id <- create_group_project(project_name, namespace_id = NULL, default_branch = "main"),
  regexp = "already exists"
)

# add_labels ----
test_that("add_labels works", {

  ## Add new
  add_labels(project_id)

  ## Add again but nothing append
  expect_message(labels <- add_labels(project_id), "No new labels to add")
  
  expect_equal(nrow(labels), 0)
  
})

# add_board ----
test_that("add_board works", {
  board <- add_board(project_id)

  expect_equal(nrow(board), 1)
})

# add_issue_clients ----
test_that("add_issue_clients works", {
  expect_message(issue <- add_issue_clients(project_id, project_name, group_url), "Issue Client")
  expect_equal(issue[["iid"]], "1")
})

# add_wikis ----
test_that("add_wikis works", {
  expect_message(
    wiki <- add_wikis(project_id, project_name, group_url, group = basename(group_url)),
    "Wiki home"
  )
  expect_equal(nrow(wiki), 3)
})

# clone_locally ----
test_that("clone_locally works", {
  expect_message(
    clone <- clone_locally(project_name, group_url, open = FALSE)
  )
  expect_true(dir.exists(clone))
  expect_true(dir.exists(file.path(clone, ".git")))
  # expect_equal(clone, project_path)
  unlink(clone, recursive = TRUE)
})

expect_error(
  project_path <- clone_locally(project_name, group_url, open = FALSE),
  regexp = NA
)

expect_message(
  r_project <- create_r_project(project_path, type = c("package"), name_licence = "test", type_licence = usethis::use_mit_license),
  "package created"
)

# push_main ----
test_that("push_main works", {
  expect_message(push_main(project_path))
  # Verify on GitLab
  branches <- gitlabr::gl_list_branches(project_id)
  expect_true(branches[["name"]] %in% c("main", "master"))
})

# create_production ----
test_that("create_production works", {
  expect_message(create_production(project_path))
  branche <- gitlabr::gl_get_branch(project_id, "production")
  expect_true(nrow(branche) > 0)
})

# protect_branches ----
test_that("protect_branches works", {
  expect_message(protect_branches(project_id))
  p_branches <- gitlab(
    req = paste0("projects/", project_id, "/protected_branches"),
    verb = httr::GET
  )
  expect_equal(p_branches[["push_access_levels.access_level"]], c("0", "0", "0"))
})

# modify_autoclose_and_coverage ----
test_that("modify_autoclose_and_coverage works", {
  expect_message(modify_autoclose_and_coverage(project_id))
})

# Modify project_options ----
test_that("project_options works", {
  expect_message(project_options(project_id), "Notification setting set for you only: watch")
})

# add_issue_dev ----
test_that("add_issue_dev works", {
  expect_message(add_issue_dev(project_id, group_url, project_name))
  issues_list <- gl_list_issues(project = project_id)
  expect_true(any(grepl("Checklist", issues_list[["title"]])))
})

# Clean
unlink(project_path, recursive = TRUE)

# Clean GitLab => Remove the project
gitlab(
  req = paste0("projects/", project_id),
  verb = httr::DELETE
)
```





```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(
  flat_file = "dev/flat_create_new_project_gitlab.Rmd",
  vignette_name = "aa - Create a new project with GitLab",
  overwrite = TRUE,
  check = FALSE,
  document = FALSE,
  open_vignette = FALSE
)

rstudioapi::navigateToFile( # Go to the dev_history_package.Rmd to inflate all flat files
  "dev/dev_history_package.Rmd",
  line = 170
)
```

