---
title: "flat_init_project_with_all.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```


```{r dev}
thinkr_config_default <- here::here("inst", "config_default_thinkr_gitlab.yml")
cat('forge: gitlab # or github
gitlab_forge_url: https://gitlab.com # URL of the GitLab forge to create project
gitlab_envt_token_name: GITLAB_PAT # Name of the environment variable to use
gitlab_namespace_id: NULL # Group id where to create the GitLab projet
github_url: https://github.com/
github_owner: NULL
owner_type: user # user or organization
github_envt_token_name: GITHUB_PAT
default_branch: main
project_type: package # or book, golem
name_licence: NULL
type_licence: usethis::use_proprietary_license
dev_history: [package, book, renv]
gitlab_ci_type: check-coverage-pkgdown # or bookdown, bookdown-production, check-coverage-pkgdown-renv. See ?gitlabr::use_gitlab_ci
bookdown_output_format: lozen::bs4_book_template  # or lozen::paged_template
github_ci: [check-standard, test-coverage, pkgdown]
deploy_connect: false
lang: fr # en - Language of issue templates, wiki, labels, ... when translated
git_production_branch: true
git_templates: ["commit", "mr"] # Whether to add commit template and (GitLab) MR template locally
gitlab_protect_branches: true
gitlab_autoclose_issue: false
gitlab_coverage_regex: "Coverage: \\\\d+\\\\.\\\\d+" # Regex in GitLab CI.
gitlab_labels: ["Blocked", "Ready"] # and others...
gitlab_board_name: "Development"
gitlab_board_labels_order: ["Bloqué", "Prêt", "En cours", "Révision", "Pré-validation", "A valider"]
github_board_columns: ["Open", "Blocked", "Meta", "Ready", "In Progress", "Review", "Validation"] # and others...
template_issue: true # Whether to include default templates to open issues
template_issue_type: ["full", "light"]
first_issue_client: true
first_issue_dev: true
issue_client: true # Whether to open an issue to explain the project to clients
issue_kickoff: true
issue_dev: true # Whether to open an issue to explain the remainig steps to prepare the project for leaddev
wiki: true # Whether to add wiki pages
wiki_types: ["home", "cr", "keys", "weekly"] # Type of wiki to add
', file = thinkr_config_default
)
config_default <- yaml::read_yaml(thinkr_config_default)

# PKG - File for unit test to verify options were changed ----
thinkr_config_package_gitlab <- here::here("inst", "thinkr_config_test_amend.yml")
cat('forge: gitlab # or github
gitlab_forge_url: https://forge.thinkr.fr # URL of the GitLab forge to create project
gitlab_envt_token_name: FORGE_THINKR_TOKEN # Name of the environment variable to use
github_owner: ThinkR-open
project_type: package # or book, golem
name_licence: ThinkR
dev_history: [package]
gitlab_ci_type: check-coverage-pkgdown
deploy_connect: false
', file = thinkr_config_package_gitlab
)
config <- yaml::read_yaml(thinkr_config_package_gitlab)
config_path <- thinkr_config_package_gitlab

thinkr_config_package_github <- here::here("inst", "thinkr_config_test_amend_github.yml")
cat('forge: github
github_url: https://github.com/
github_owner: ThinkR-open
owner_type: organization
github_envt_token_name: GITHUB_PAT
project_type: package
name_licence: ThinkR
dev_history: [package]
github_ci: [check-standard, test-coverage, pkgdown]
', file = thinkr_config_package_github
)
config <- yaml::read_yaml(thinkr_config_package_github)
config_path <- thinkr_config_package_github

# BOOK - File for unit test to verify options where changed ----
thinkr_config_book_gitlab <- here::here("inst", "thinkr_config_book_gitlab.yml")
cat('forge: gitlab # or github
gitlab_forge_url: https://forge.thinkr.fr # URL of the GitLab forge to create project
gitlab_envt_token_name: FORGE_THINKR_TOKEN # Name of the environment variable to use
github_owner: ThinkR-open
project_type: book # or book, golem
name_licence: ThinkR
dev_history: [package]
gitlab_ci_type: bookdown-production
bookdown_output_format: lozen::bs4_book_template  # or lozen::paged_template
deploy_connect: false
', file = thinkr_config_book_gitlab
)
yaml::read_yaml(thinkr_config_book_gitlab)
```

# Init a new project with everything in one command

`init_project_with_all()` will follow the ThinkR recommended configuration to init a new project.
By default, the project is a R package created on <https://gitlab.com/> in your personal repository.  
After that, you only have to start writing the code ! 

You can amend the default configuration with your own yaml file.
Open the default one: `file.edit(system.file("config_default_thinkr_gitlab.yml", package = "lozen"))`.  
Keep only lines that you would like to change, and save your own configuration where you like it to be.  
Next time you can run `init_project_with_all(project_name = "my.wonderful.project", config_path = "path/to/my/own/config.yaml")`. 

```{r function-init_project_with_all}
#' Init a new project with everything in one command
#' 
#' @param project_name The name of the project to be created
#' @param project_gitlab_id GitLab ID of the project if it already exist on your Forge
#' @param config_path The path to the yaml configuration file to use with your options to modify the default one. See details.
#' @param project_path The path to the project if your want to keep it locally. Default to temporary directory.
#' @param ... Any parameter existing in the configuration file that you would like to use to override your config files
#' @details By default, the project is a R package created on <https://gitlab.com/about/> in your personal repository. Use your own configuration file to amend the default one. 
#' The configuration file is a yaml file with all possible options. You do not have to specify all options as it will be combined with our default ones. Open the default one to see what is in it: `file.edit(system.file("config_default_thinkr_gitlab.yml", package = "lozen"))`
#' 
#' 
#' @importFrom yaml read_yaml
#' @importFrom purrr list_modify pluck
#' @importFrom cli cli_text cli_li cli_alert_info
#' @importFrom gitlabr gl_connection set_gitlab_connection gl_get_project
#' @importFrom usethis with_project use_github_action use_r
#' @importFrom gert git_config_set
#' @importFrom glue glue
#' @importFrom gh gh_gql
#' @importFrom yesno yesno
#' @importFrom golem add_rstudioconnect_file
#' @importFrom withr with_dir
#' 
#' @export
init_project_with_all <- function(project_name, project_gitlab_id = NULL, config_path,
                                  project_path = tempfile('clone'), ...) {
  # Read ThinkR default in package
  config_default <- read_yaml(system.file("config_default_thinkr_gitlab.yml", package = "lozen"))
  if (!missing(config_path)) {
    config_user <- read_yaml(config_path)
    # Combine with user config file so that they do not have to define everything
    config <- list_modify(config_default, !!!config_user)
  } else {
    config <- config_default
  }
  # Override with ...
  config_local_dots <- list(...)
  config <- list_modify(config, !!!config_local_dots)

  forge <- tolower(config$forge)
  if (is.null(config$gitlab_namespace_id) || config$gitlab_namespace_id == "") {
    namespace_type = "user"
  } else {
    namespace_type = paste("group with id:", config$gitlab_namespace_id)
  }

  cat(cli_text("You are about to create a new project with these configuration:"),
      cli_li(c(
        paste("Forge:", forge),
        ifelse(
          forge == "gitlab",
          paste("Forge URL: ", config$gitlab_forge_url),
          paste("GitHub: ", config$github_url)
        ),
        ifelse(
          forge == "gitlab",
          paste("namespace: ", namespace_type),
          paste("GitHub Owner (", config$owner_type, "): ", config$github_owner)
        ),
        paste("project_name: ", project_name),
        paste("project_type: ", config$project_type)
      ))
  )
  # warning for manual steps
  if (forge == "github"){
    cli_alert_warning("Make sure you confirm all the manual steps to create the project")
  }
  answer <- readline("Are you ok with that? (y/n)")
  if (answer %in% c("n", "no")) {message("You stopped the process"); return(NULL)}

  # Connect to GitLab ----
  if (forge == "gitlab") {
    # Init GitLab
    gitlab_url <- Sys.getenv("GITLAB_URL", unset = config$gitlab_forge_url)

    # GitLab con
    my_gitlab <- gl_connection(
      gitlab_url = gitlab_url,
      private_token = Sys.getenv(config$gitlab_envt_token_name)
    )

    # Set the connection for the session
    set_gitlab_connection(my_gitlab)

    # Create / Connect project on GitLab ----
    if (is.null(project_gitlab_id)) {
      # If project does not exist
      project_id <- create_group_project(
        project_name = project_name,
        namespace_id = config$gitlab_namespace_id,
        default_branch = config$default_branch
      )
    }
    the_project <- gl_get_project(
      project = project_id
    )

    project_name <- the_project[["name"]]
    group_url <- gsub(the_project[["name"]], "", the_project[["web_url"]])
    project_url <- the_project$web_url
  }

  # Connect to GitHub ----
  if (forge == "github") {
    # GitHub con
    project_url <- paste(
      config$github_url,
      config$github_owner,
      project_name,
      sep = "/"
    )

    # Create / Connect project on GitHub ----
    project_id <- create_group_project_github(
      repo = project_name,
      owner = config$github_owner
      )

    group_url <- paste(
      config$github_url,
      config$github_owner,
      sep = "/"
    )
  }

  # Retrieve project locally
  project_path <- clone_locally(
    project_name = project_name,
    project_path = file.path(tempfile('clone'), project_name),
    group_url = group_url,
    open = FALSE
  )

  # Create the project
  create_r_project(
    project_path,
    type = config$project_type,
    name_licence = config$name_licence,
    type_licence = eval(parse(text = config$type_licence))
  )
  
  # Add a piece of code to pass codecov
  with_project(
    path = project_path,
    code = {use_r(name = "start", open = FALSE)}
  )
  
  # Add extra dev_history
  use_dev_history(path = project_path, type = config$dev_history)

  # Set up CI GitLab ----
  if (forge == "gitlab") {
    lozen::use_gitlab_ci(
      project_path = project_path,
      type = config$gitlab_ci_type,
      bookdown_output_format = config$bookdown_output_format
    )
  }

  # Set up CI GitHub ----
  if (forge == "github") {
    with_project(
      path = project_path,
      code = {
        sapply(
          X = config$github_ci,
          FUN = \(x) {use_github_action(
            name = x,
            badge = FALSE # requires readme file
          )})
      }
    )
  }

  # What to deploy on Connect GitLab ----
  if (forge == "gitlab") {
    if (isTRUE(config$deploy_connect)) {
      message("Note that you will need to specify some required environment variables in your GitLab project")
      # Deploy book if book
      if (config$project_type == "book") {
        with_dir(project_path, {
          lozen::use_gitlab_ci_deploy_connect_bookdown()
        })
      }
      # Deploy pkgdown if package
      if (config$project_type == "package") {
        with_dir(project_path, {
          lozen::use_gitlab_ci_deploy_connect_pkgdown()
        })
      }
      # Deploy app if golem
      if (config$project_type == "golem") {
        with_dir(project_path, {
          golem::add_rstudioconnect_file(pkg = project_path)
          use_gitlab_ci_deploy_connect_shiny()
        })
      }
    }
  }

  # Commit and MR templates ----
  if (!is.null(config$git_templates) || config$git_templates != "") {
    add_git_templates(
      project_path = project_path,
      type = config$git_templates,
      target_dir = paste0(".", forge)
    )
  }
  
  # Issue template
  if (!is.null(config$template_issue_type) ||
      config$template_issue_type != "") {
    if (forge == "gitlab") {
      gl_add_template_issue(
        project_path = project_path,
        language = config$lang,
        # "fr" # you can use "en" instead
        type = config$template_issue_type
      )
    }
    if (forge == "github") {
      sapply(X = config$template_issue_type,
             FUN = \(x) {
               gh_add_template_issue(
                 project_path = project_path,
                 language = config$lang,
                 # "fr" # you can use "en" instead
                 type = x
               )
             })
    }
  }
  
  # Name branch and push to server ----
  git_config_set(
    name = "init.defaultbranch",
    value = config$default_branch,
    repo = project_path
  )
  push_main(
    project_path = project_path
  )

  # Add production branch
  if (isTRUE(config$git_production_branch)) {
    create_production(
      project_path = project_path
    )
  }

  # Git configuration GitLab ----
  if (forge == "gitlab") {
    # Protect branches ----
    if (isTRUE(config$gitlab_protect_branches)) {
      protect_branches(
        project_id = project_id
      )
    }

    # Autoclose and coverage ----
    if (isTRUE(config$gitlab_protect_branches)) {
      modify_autoclose_and_coverage(
        project_id = project_id,
        autoclose = config$gitlab_autoclose_issue,
        build_coverage_regex = config$gitlab_coverage_regex
      )
    }
  }

  # Git configuration GitHub ----
  if (forge == "github") {
    # Protect branches ----
    protect_url <- paste0(
      project_url,
      "/settings/branch_protection_rules/new?branch_name=",
      config$default_branch
    )
    cli_alert_info(text = "To protech your branch, please visit :\n {.url {protect_url}}")
    continue <- yesno("Manual step in progress : protecting branch. Can we continue ?")
    if (isFALSE(continue)) {message("You stopped the process"); return(NULL)}
  }
  
  # GitLab project setup ----
  if (forge == "gitlab") {
    add_labels(
      project_id = project_id,
      lg = config$lang
    )

    add_board(
      project_id = project_id,
      name = config$gitlab_board_name,
      labels_order = config$gitlab_board_labels_order,
      lg = config$lang
    )
  }
  
  # GitHub project setup ----
  if (forge == "github") {
    # Create project/board from graphql api
    # fetch user/orga node id
    req_user_node_id <- glue(
      'query{
        $_owner_type_$(login: "$_organization_$"){
          id
        }
      }',
      .open = "$_",
      .close = "_$",
      owner_type = config$owner_type,
      organization = config$github_owner,
      )
    
    user_node_id <- gh_gql(
      query = req_user_node_id,
      .token = Sys.getenv(config$github_envt_token_name)
      ) %>%
      pluck("data", config$owner_type, "id")
    
    # emit warning if node id is not found
    if (is.null(user_node_id)) {
      cli_alert_warning("Failed to fetch {config$github_owner} as a GitHub {config$owner_type}")
    }

    # create board
    req_project_create <- glue(
      'mutation{
        createProjectV2(
          input: {
            ownerId: "$_user_node_id_$",
            title: "$_project_name_$"
          }
        ){
          projectV2 {
            id
            number
          }
         }
      }',
      .open = "$_",
      .close = "_$")
    
    project_id <- gh::gh_gql(
      query = req_project_create,
      .token = Sys.getenv(config$github_envt_token_name)
      )
    project_id <- project_id %>%
      pluck("data", "createProjectV2", "projectV2")

    # Notify user of the remaining manual steps
    proj_url <- paste0(project_url, "/projects")
    cli_alert_info(
      "The project board has been created, you can link it to the repo here :
                        {.url {proj_url}}
                        You can search for the project {.emph {project_name}} after clicking on {.emph Link a project}"
    )
    continue <- yesno("Manual step in progress : linking project to repo. Can we continue ?")
    if (isFALSE(continue)) {
      message("You stopped the process")
      return(NULL)
    }
    
    cli_alert_info("The following columns of the project should be manually added :")
    cli_li(config$github_board_columns)
    continue <- yesno("Manual step in progress : adding columns to project. Can we continue ?")
    if (isFALSE(continue)) {
      message("You stopped the process")
      return(NULL)
    }
  }

  # Special issues and wiki GitHub ----
  if (forge == "github") {
    if (isTRUE(config$issue_client)) {
      add_issue_clients_github(
        owner = config$github_owner,
        repo = project_name
      )
    }
    
    if (isTRUE(config$issue_kickoff)) {
      add_issue_kickoff_github(
        owner = config$github_owner,
        repo = project_name
      )
    }
    
    if (isTRUE(config$issue_dev)) {
      add_issue_dev_github(
        owner = config$github_owner,
        repo = project_name
      )
    }
    
    # Link issues to project on GitHub
    if (forge == "github") {
      issue_url <- paste0(project_url, "/issues")
      cli_alert_info("You need to assign the new issues to the project board. :
                  {.url {issue_url}}")
      continue <- yesno("Manual step in progress : linking issue to project. Can we continue ?")
      if (isFALSE(continue)) {
        message("You stopped the process")
        return(NULL)
      }
    }
    
    if (isTRUE(config$wiki)) {
      add_wikis_github(
        owner = config$github_owner,
        repo = project_name,
        type = config$wiki_types
      )
    }
  }

  # Special issue and wiki GitLab
  if (forge == "gitlab") {
    if (isTRUE(config$issue_client)) {
      add_issue_clients(
        project_id = project_id,
        project_name = project_name,
        group_url = group_url
      )
    }
    
    if (isTRUE(config$issue_kickoff)) {
      add_issue_kickoff(
        project_id = project_id
      )
    }
    
    if (isTRUE(config$issue_dev)) {
      add_issue_dev(
        project_id = project_id,
        group_url = group_url,
        project_name = project_name
      )
    }
    
    if (isTRUE(config$wiki)) {
      add_wikis(
        project_id = project_id,
        project_name = project_name,
        group_url = group_url,
        group = basename(group_url),
        type = config$wiki_types
      )
    }
  }
  
  cat(
    cli::cli_text("Find your project on: {.url  {project_url}} ")
  )

  return(list(project_url = project_url,
              project_path = project_path))
}

```

```{r example-init_project_with_all, eval=FALSE}
if (interactive()) {
  # Default on GitLab.com
  init_project_with_all(project_name = "newprojectpkg")
  # Change default options with your own config file
  init_project_with_all(project_name = "newprojectpkg", config_path = "<my-config-path>")
  # Add any extra option to override values of your config file once
  init_project_with_all(project_name = "newprojectpkg", config_path = "<my-config-path>", gitlab_namespace_id = "000")
}
```

```{r test-init_project_with_all}
test_that("init_project_with_all can be used for package in interactive session", {
  if (interactive()) {
    answer <- readline("Do you want to test if `init_project_with_all()` works for packages on GitLab ? (y/n)")
    if (answer %in% c("n", "no")) {skip()}
    
    init_project_with_all(
      project_name = "newprojecttest", 
      config_path = system.file("thinkr_config_test_amend.yml", package = "lozen"),
      gitlab_namespace_id = 1013)
    
    cat("Manual test: The project should be a R package with CI and pkgdown on GitLab. There are wikis, issues opened, and templates issues. There is a board of issues.",
            "\nAfter that, you can delete the project.")
    answer <- readline("Is the package project correctly initiated and deployed ? (y/n)")
    expect_true(answer %in% c("y", "yes"))
    
    
    answer <- readline("Do you want to test if `init_project_with_all()` works for packages on GitHub ThinkR-open account ? (y/n)")
    if (answer %in% c("n", "no")) {skip()}
    init_project_with_all(
      project_name = "testinitalllozen",
      config_path = system.file("thinkr_config_test_amend_github.yml", package = "lozen")
      )
    
    cat("Manual test: The project should be a R package with CI and pkgdown on GitHub. There are wikis, issues opened, and templates issues. There is a board of issues.",
        "\nAfter that, you can delete the repo and project.")
    answer <- readline("Is the package project correctly initiated ? (y/n)")
    expect_true(answer %in% c("y", "yes"))
    
  }
})

test_that("init_project_with_all can be used for books in interactive session", {
  if (interactive()) {
    answer <- readline("Do you want to test if `init_project_with_all()` works for books? (y/n)")
    if (answer %in% c("n", "no")) {skip()}
    
    init_project_with_all(
      project_name = "newbooktest", 
      config_path = system.file("thinkr_config_book_gitlab.yml", package = "lozen"))
    
    cat("Manual test: The project should be a R bookdown with CI and bookd deployed on GitLab. There are wikis, issues opened, and templates issues. There is a board of issues.",
            "\nAfter that, you can delete the project.")
    answer <- readline("Is the book project correctly initiated and deployed ? (y/n)")
    expect_true(answer %in% c("y", "yes"))
  }
})
```



```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_init_project_with_all.Rmd", vignette_name = "aa - Launch full project - all in one", check = FALSE, open_vignette = FALSE, overwrite = TRUE)
```

