---
title: "flat_init_project_with_all.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```


```{r dev}
thinkr_config_default <- here::here("inst", "config_default_thinkr_gitlab.yml")
cat('forge: gitlab # or github
gitlab_forge_url: https://gitlab.com # URL of the GitLab forge to create project
gitlab_envt_token_name: GITLAB_PAT # Name of the environment variable to use
gitlab_namespace_id: NULL # Group id where to create the GitLab projet
github_url: https://github.com/
github_owner: NULL
default_branch: main
project_type: package # or book, golem
name_licence: NULL
type_licence: usethis::use_proprietary_license
dev_history: [package, book, renv]
gitlab_ci_type: check-coverage-pkgdown # or bookdown, bookdown-production, check-coverage-pkgdown-renv. See ?gitlabr::use_gitlab_ci
bookdown_output_format: lozen::bs4_book_template  # or lozen::paged_template
github_ci: [check-standard, test-coverage, pkgdown]
deploy_connect: false
lang: fr # en - Language of issue templates, wiki, labels, ... when translated
git_production_branch: true
git_templates: ["commit", "mr"] # Whether to add commit template and (GitLab) MR template locally
gitlab_protect_branches: true
gitlab_autoclose_issue: false
gitlab_coverage_regex: "Coverage: \\\\d+\\\\.\\\\d+" # Regex in GitLab CI.
gitlab_labels: ["Blocked", "Ready"] # and others...
gitlab_board_name: "Development"
gitlab_board_labels_order: ["Bloqué", "Prêt", "En cours", "Révision", "Pré-validation", "A valider"]
github_board_columns: ["Open", "Blocked", "Meta", "Ready", "In Progress", "Review", "Validation"] # and others...
template_issue: true # Whether to include default templates to open issues
template_issue_type: ["full", "light"]
first_issue_client: true
first_issue_dev: true
issue_client: true # Whether to open an issue to explain the project to clients
issue_kickoff: true
issue_dev: true # Whether to open an issue to explain the remainig steps to prepare the project for leaddev
wiki: true # Whether to add wiki pages
wiki_types: ["home", "cr", "keys", "weekly"] # Type of wiki to add
', file = thinkr_config_default
)
config_default <- yaml::read_yaml(thinkr_config_default)

# PKG - File for unit test to verify options were changed ----
thinkr_config_package_gitlab <- here::here("inst", "thinkr_config_test_amend.yml")
cat('forge: gitlab # or github
gitlab_forge_url: https://forge.thinkr.fr # URL of the GitLab forge to create project
gitlab_envt_token_name: FORGE_THINKR_TOKEN # Name of the environment variable to use
github_owner: ThinkR-open
project_type: package # or book, golem
name_licence: ThinkR
dev_history: [package]
gitlab_ci_type: check-coverage-pkgdown
deploy_connect: false
', file = thinkr_config_package_gitlab
)
config <- yaml::read_yaml(thinkr_config_package_gitlab)
config_path <- thinkr_config_package_gitlab

# BOOK - File for unit test to verify options where changed ----
thinkr_config_book_gitlab <- here::here("inst", "thinkr_config_book_gitlab.yml")
cat('forge: gitlab # or github
gitlab_forge_url: https://forge.thinkr.fr # URL of the GitLab forge to create project
gitlab_envt_token_name: FORGE_THINKR_TOKEN # Name of the environment variable to use
github_owner: ThinkR-open
project_type: book # or book, golem
name_licence: ThinkR
dev_history: [package]
gitlab_ci_type: bookdown-production
bookdown_output_format: lozen::bs4_book_template  # or lozen::paged_template
deploy_connect: false
', file = thinkr_config_book_gitlab
)
yaml::read_yaml(thinkr_config_book_gitlab)
```

# Init a new project with everything in one command

`init_project_with_all()` will follow the ThinkR recommended configuration to init a new project.
By default, the project is a R package created on <https://gitlab.com/> in your personal repository.  
After that, you only have to start writing the code ! 

You can amend the default configuration with your own yaml file.
Open the default one: `file.edit(system.file("config_default_thinkr_gitlab.yml", package = "lozen"))`.  
Keep only lines that you would like to change, and save your own configuration where you like it to be.  
Next time you can run `init_project_with_all(project_name = "my.wonderful.project", config_path = "path/to/my/own/config.yaml")`. 

```{r function-init_project_with_all}
#' Init a new project with everything in one command
#' 
#' @param project_name The name of the project to be created
#' @param project_gitlab_id GitLab ID of the project if it already exist on your Forge
#' @param config_path The path to the yaml configuration file to use with your options to modify the default one. See details.
#' @param project_path The path to the project if your want to keep it locally. Default to temporary directory.
#' @param ... Any parameter existing in the configuration file that you would like to use to override your config files
#' @details By default, the project is a R package created on <https://gitlab.com/about/> in your personal repository. Use your own configuration file to amend the default one. 
#' The configuration file is a yaml file with all possible options. You do not have to specify all options as it will be combined with our default ones. Open the default one to see what is in it: `file.edit(system.file("config_default_thinkr_gitlab.yml", package = "lozen"))`
#' 
#' 
#' @importFrom yaml read_yaml
#' @importFrom purrr list_modify pluck
#' @importFrom cli cli_text cli_li
#' @importFrom gitlabr gl_connection set_gitlab_connection gl_get_project
#' @importFrom usethis with_project use_github_action
#' @importFrom gert git_config_set
#' @importFrom glue glue
#' @importFrom gh gh_gql
#' 
#' @export
init_project_with_all <- function(project_name, project_gitlab_id = NULL, config_path,
                                  project_path = tempfile('clone'), ...) {
  # Read ThinkR default in package
  config_default <- yaml::read_yaml(system.file("config_default_thinkr_gitlab.yml", package = "lozen"))
  if (!missing(config_path)) {
    config_user <- yaml::read_yaml(config_path)
    # Combine with user config file so that they do not have to define everything
    config <- purrr::list_modify(config_default, !!!config_user)
  } else {
    config <- config_default
  }
  # Override with ...
  config_local_dots <- list(...)
  config <- purrr::list_modify(config, !!!config_local_dots)
  
  forge <- tolower(config$forge)
  if (is.null(config$gitlab_namespace_id) || config$gitlab_namespace_id == "") {
    namespace_type = "user"
  } else {
    namespace_type = paste("group with id:", config$gitlab_namespace_id)
  }
  
  cat(
    cli::cli_text("You are about to create a new project with these configuration:"),
    cli::cli_li(c(
      paste("Forge:", forge),
      ifelse(forge == "gitlab", paste("Forge URL: ", config$gitlab_forge_url),
                   paste("GitHub: ", config$github_url)),
      ifelse(forge == "gitlab", paste("namespace: ", namespace_type),
                   paste("GitHub Owner: ", config$github_owner)),
      paste("project_name: ", project_name),
      paste("project_type: ", config$project_type)
    ))
  )
  answer <- readline("Are you ok with that? (y/n)")
  if (answer %in% c("n", "no")) {message("You stopped the process"); return(NULL)}
  
  # Connect to GitLab ----
  if (forge == "gitlab") {
    # Init GitLab
    gitlab_url <- Sys.getenv("GITLAB_URL", unset = config$gitlab_forge_url)
    
    # GitLab con
    my_gitlab <- gl_connection(
      gitlab_url = gitlab_url,
      private_token = Sys.getenv(config$gitlab_envt_token_name)
    )
    
    # Set the connection for the session
    set_gitlab_connection(my_gitlab)
    
    
    # Create / Connect project on GitLab ----
    if (is.null(project_gitlab_id)) {
      # If project does not exist
      project_id <- create_group_project(
        project_name = project_name,
        namespace_id = config$gitlab_namespace_id,
        default_branch = config$default_branch
      )
    } 
    the_project <- gl_get_project(
      project = project_id
    )
    
    project_name <- the_project[["name"]]
    group_url <- gsub(the_project[["name"]], "", the_project[["web_url"]])
    project_url <- the_project$web_url
  }
  
  # Connect to GitHub ----
  if (forge == "github") {
    # GitHub con
    project_url <- paste(
      config$github_url,
      config$github_owner,
      project_name,
      sep = "/"
    )
    
    # Create / Connect project on GitHub ----
    project_id <- create_group_project_github(
      repo = project_name,
      owner = config$github_owner
      )
    
    group_url <- paste(
      config$github_url,
      config$github_owner,
      sep = "/"
    )
  }
  
  # Retrieve project locally
  project_path <- clone_locally(
    project_name = project_name,
    project_path = file.path(tempfile('clone'), project_name),
    group_url = group_url,
    open = FALSE
  )
  
  # Create the project
  create_r_project(
    project_path,
    type = config$project_type,
    name_licence = config$name_licence,
    type_licence = eval(parse(text = config$type_licence))
  )
  
  # Add extra dev_history
  use_dev_history(path = project_path, type = config$dev_history)
  
  # Set up CI GitLab ----
  if (forge == "gitlab") {
    lozen::use_gitlab_ci(
      project_path = project_path,
      type = config$gitlab_ci_type,
      bookdown_output_format = config$bookdown_output_format
    )
  }
  
  # Set up CI GitHub ----
  if (forge == "github") {
    usethis::with_project(
      path = project_path,
      code = {
        sapply(
          X = config$github_ci,
          FUN = \(x) {usethis::use_github_action(
            name = x,
            badge = FALSE # requires readme file
          )})
      }
    )
  }
  
  # What to deploy on Connect ----
  if (forge == "gitlab") {
    if (isTRUE(config$deploy_connect)) {
      message("Note that you will need to specify some required environment variables in your GitLab project")
      # Deploy book if book
      if (config$project_type == "book") {
        withr::with_dir(project_path, {
          lozen::use_gitlab_ci_deploy_connect_bookdown()
        })
      }
      # Deploy pkgdown if package
      if (config$project_type == "package") {
        withr::with_dir(project_path, {
          lozen::use_gitlab_ci_deploy_connect_pkgdown()
        })
      }
      # Deploy app if golem
      if (config$project_type == "golem") {
        withr::with_dir(project_path, {
          golem::add_rstudioconnect_file(pkg = project_path)
          use_gitlab_ci_deploy_connect_shiny()
        })
      }
    }
  }
  
  # Commit and MR templates ---- 
  if (!is.null(config$git_templates) || config$git_templates != "") {
    add_git_templates(
      project_path = project_path,
      type = config$git_templates
    )
  }
  
  # Name branch and push to server ----
  gert::git_config_set(
    name = "init.defaultbranch",
    value = config$default_branch,
    repo = project_path
    )
  push_main(
    project_path = project_path
  )
  
  if (isTRUE(config$git_production_branch)) {
    create_production(
      project_path = project_path
    )
  }
  
  # Git configuration ----
  if (forge == "gitlab") {
    # Protect branches ----
    if (isTRUE(config$gitlab_protect_branches)) {
      protect_branches(
        project_id = project_id
      )
    }
    
    # Autoclose and coverage ----
    if (isTRUE(config$gitlab_protect_branches)) {
      modify_autoclose_and_coverage(
        project_id = project_id,
        autoclose = config$gitlab_autoclose_issue,
        build_coverage_regex = config$gitlab_coverage_regex
      )
    }
  }
  
  if (forge == "gitlab") {
    if (!is.null(config$template_issue_type) || config$template_issue_type != "") {
      gl_add_template_issue(
        project_path = project_path,
        language = config$lang, # "fr" # you can use "en" instead
        type = config$template_issue_type
      )
    }
  }
  
  # GitLab project setup ----
  if (forge == "gitlab") {
    add_labels(
      project_id = project_id,
      lg = config$lang
    )
    
    add_board(
      project_id = project_id,
      name = config$gitlab_board_name,
      labels_order = config$gitlab_board_labels_order,
      lg = config$lang
    )
    
    if (isTRUE(config$issue_client)) {
      add_issue_clients(
        project_id = project_id,
        project_name = project_name,
        group_url = group_url
      )
    }
    
    if (isTRUE(config$issue_kickoff)) {
      add_issue_kickoff(
        project_id = project_id
      )
    }
    
    if (isTRUE(config$issue_dev)) {
      add_issue_dev(
        project_id = project_id,
        group_url = group_url,
        project_name = project_name
      )
    }
    
    if (isTRUE(config$wiki)) {
      add_wikis(
        project_id = project_id,
        project_name = project_name,
        group_url = group_url,
        group = basename(group_url),
        type = config$wiki_types
      )
    }
  }
  # GitHub project setup ----
  if (forge == "github") {
    # add_labels(
    #   project_id = project_id,
    #   lg = config$lang
    # )

    # Create project/board from graphql api
    github_token <- Sys.getenv(config$gitlab_envt_token_name)
    organization <- config$github_owner
    # fetch user id
    req_user_node_id <- glue(
      'query{
        user(login: "$_organization_$"){
          id
        }
      }',
      .open = "$_",
      .close = "_$")
    user_node_id <- gh::gh_gql(req_user_node_id, .token = github_token) %>% 
      purrr::pluck("data", "user", "id")
    
    # create board
    req_project_create <- glue(
      'mutation{
        createProjectV2(
          input: {
            ownerId: "$_user_node_id_$",
            title: "$_project_name_$"
          }
        ){
          projectV2 {
            id
          }
         }
      }', 
      .open = "$_",
      .close = "_$")
    project_id <- gh::gh_gql(req_project_create, .token = github_token) %>% 
      purrr::pluck("data", "createProjectV2", "projectV2", "id")

    # Add first issues for dev and client
    if (isTRUE(config$issue_client)) {
      add_issue_clients_github(
        owner = config$github_owner,
        repo = project_name
      )
    }
    
    if (isTRUE(config$issue_kickoff)) {
      add_issue_kickoff_github(
        owner = config$github_owner,
        repo = project_name
      )
    }
    
    if (isTRUE(config$issue_dev)) {
      add_issue_dev_github(
        owner = config$github_owner,
        repo = project_name
      )
    }
    
    if (isTRUE(config$wikis)) {
      add_wikis_github(
        owner = config$github_owner,
        repo = project_name,
        type = config$wiki_types
      )
    }
    
    # List the last manual edits to the user
    cli::cli_text("You need to link the board to the repo in <", project_url ,"/projects>.")
    cli::cli_text("You need to assign the issues to the board.")
    cli::cli_text("You need to add the columns ", paste0(config$github_board_columns, collapse = ", ") ," to the board.")
  }
  
  cat(
    cli::cli_text("Find your project on: {.url  {project_url}} ")
  )
  
  return(list(project_url = project_url,
              project_path = project_path))
}

```

```{r example-init_project_with_all, eval=FALSE}
if (interactive()) {
  # Default on GitLab.com
  init_project_with_all(project_name = "newprojectpkg")
  # Change default options with your own config file
  init_project_with_all(project_name = "newprojectpkg", config_path = "<my-config-path>")
  # Add any extra option to override values of your config file once
  init_project_with_all(project_name = "newprojectpkg", config_path = "<my-config-path>", gitlab_namespace_id = "000")
}
```

```{r test-init_project_with_all}
test_that("init_project_with_all can be used for package in interactive session", {
  if (interactive()) {
    answer <- readline("Do you want to test if `init_project_with_all()` works for packages on GitLab ? (y/n)")
    if (answer %in% c("n", "no")) {skip()}
    
    init_project_with_all(
      project_name = "newprojecttest", 
      config_path = system.file("thinkr_config_test_amend.yml", package = "lozen"),
      gitlab_namespace_id = 1013)
    
    cat("Manual test: The project should be a R package with CI and pkgdown on GitLab. There are wikis, issues opened, and templates issues. There is a board of issues.",
            "\nAfter that, you can delete the project.")
    answer <- readline("Is the package project correctly initiated and deployed ? (y/n)")
    expect_true(answer %in% c("y", "yes"))
    
    
    answer <- readline("Do you want to test if `init_project_with_all()` works for packages on GitHub ? (y/n)")
    if (answer %in% c("n", "no")) {skip()}
    
    init_project_with_all(
      project_name = "newprojecttest", 
      config_path = system.file("thinkr_config_test_amend_github.yml", package = "lozen"),
      gitlab_namespace_id = NULL)
    
    cat("Manual test: The project should be a R package with CI and pkgdown on GitHub. There are wikis, issues opened, and templates issues. There is a board of issues.",
        "\nAfter that, you can delete the project.")
    answer <- readline("Is the package project correctly initiated and deployed ? (y/n)")
    expect_true(answer %in% c("y", "yes"))
    
  }
})

test_that("init_project_with_all can be used for books in interactive session", {
  if (interactive()) {
    answer <- readline("Do you want to test if `init_project_with_all()` works for books? (y/n)")
    if (answer %in% c("n", "no")) {skip()}
    
    init_project_with_all(
      project_name = "newbooktest", 
      config_path = system.file("thinkr_config_book_gitlab.yml", package = "lozen"))
    
    cat("Manual test: The project should be a R bookdown with CI and bookd deployed on GitLab. There are wikis, issues opened, and templates issues. There is a board of issues.",
            "\nAfter that, you can delete the project.")
    answer <- readline("Is the book project correctly initiated and deployed ? (y/n)")
    expect_true(answer %in% c("y", "yes"))
  }
})
```



```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_init_project_with_all.Rmd", vignette_name = "aa - Launch full project - all in one", check = FALSE, open_vignette = FALSE, overwrite = TRUE)
```

