---
title: "dev/flat_helper_testthat.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all()
```


# Test gitlab CI workflows

This functions `with_gitlab_project()` allows its users to launch an
expression to initiate a given gitlab ci workflow within a dummy project on a gitlab instance.

```{r function-with_gitlab_project}
#' Test gitlab CI workflows
#'
#' This functions allows its users to launch an
#' expression to initiate a given gitlab ci workflow within a dummy project on a #' gitlab instance.
#'
#' @param gitlab_url A character string. The url of the gilab instance.
#' @param namespace_id An integer. The id of the gitlab group to
#' create the project in.
#' @param private_token A character string. The token to gain access to the
#' gitlab api.
#' @param connect_url A character string. The URL to the Connect server.
#' @param connect_api_token A character string. The token to gain access to the
#' Connect API. The token must be granted admin access.
#' @param connect_user A character string. User name on Connect.
#' @param connect_name A character string. Name of the Connect server (default "connect")
#' @param github_pat A character string. The token to gain access to the
#' github api.
#' @param project_name A character string. The name of the project to be created.
#' @param branch_focus_for_ci Name of the branch to be targeted for the CI pipeline.
#' @param exp A valid R expression initializing a project and a gitlab ci
#' workflow.
#'
#' @return A data.frame containing information about jobs of
#' the gitlab project.
#'
#' @importFrom gitlabr set_gitlab_connection unset_gitlab_connection gl_get_project gitlab
#' @importFrom cli cat_rule
#' @importFrom withr with_dir
#' @importFrom httr GET DELETE add_headers
#' @importFrom stringr str_detect
#'
#' @export
with_gitlab_project <- function(
  gitlab_url = Sys.getenv("GITLAB_URL", unset = "https://gitlab.com"),
  namespace_id,
  private_token = Sys.getenv("GITLAB_TOKEN"),
  connect_url = Sys.getenv(
    "CONNECT_URL"
  ),
  connect_api_token = Sys.getenv(
    "CONNECT_TOKEN"
  ),
  connect_user = Sys.getenv(
    "CONNECT_USER"
  ),
  connect_name = Sys.getenv(
    "CONNECT_NAME",
    unset = "connect"
  ),
  github_pat = Sys.getenv(
    "GITHUB_PAT"
  ),
  project_name = "lozen.test.project",
  branch_focus_for_ci = "main",
  exp
    ) {
  # get project name
  unique_project_name <- paste0(project_name, as.numeric(Sys.time()))

  # Have to set a API token for connect
  stopifnot("connect_api_token is unset" = connect_api_token != "")
  stopifnot("connect_url is unset" = connect_url != "")
  stopifnot("connect_user is unset" = connect_user != "")
  stopifnot("connect_name is unset" = connect_name != "")
  stopifnot("github_pat is unset" = github_pat != "")


  # Set the connection and create a new project
  set_gitlab_connection(
    gitlab_url = gitlab_url,
    private_token = private_token
  )

  project_id <- create_group_project(
    project_name = unique_project_name,
    default_branch = "main",
    namespace_id = namespace_id
  )

  # Create env var into gitlab project

  lapply(c("CONNECT_TOKEN", "CONNECT_URL", "CONNECT_USER", "CONNECT_NAME", "GITHUB_PAT"), function(x) {
    get_or_create_var_env_gitlab(
      project_id,
      x,
      Sys.getenv(x)
    )
  })

  lapply(c("APP_NAME"), function(x) {
    get_or_create_var_env_gitlab(
      project_id,
      x,
      project_name
    )
  })



  on.exit(
    {
      # Delete the gitlab project
      gitlab(
        req = paste0("projects/", project_id),
        verb = httr::DELETE
      )
      unset_gitlab_connection()
    },
    add = TRUE
  )

  ## Create tmp dir
  tmpdir <- tempfile(pattern = "lozen-test-project-")
  dir.create(tmpdir)
  project_path <- file.path(tmpdir, unique_project_name)
  on.exit(
    {
      ## Clean the tmpdir
      unlink(project_path, recursive = TRUE)
    },
    add = TRUE
  )

  ## Clone in tmp dir
  gitlab_project <- gl_get_project(project = project_id)
  group_url <- gsub(gitlab_project[["name"]], "", gitlab_project[["web_url"]])
  clone_locally(
    project_name = unique_project_name,
    group_url = group_url,
    project_path = project_path,
    open = FALSE
  )

  with_dir(
    project_path,
    {
      force(exp)
    }
  )

  ## Push to the remote
  push_all_to_branch(
    project_path,
    branch = "main",
    message = "Init repo"
  )

  ## If the CI must be tested on a specific branch
  if (branch_focus_for_ci != "main") {
    push_all_to_branch(
      project_path,
      branch = "production",
      message = paste0("Init repo - ", branch_focus_for_ci)
    )
  }

  Sys.sleep(3)
  ## Test the CI here: Is it successful?
  jobs <- gitlab(
    req = paste0("projects/", project_id, "/jobs"),
    verb = httr::GET
  )[
    1,
  ]

  if (ncol(jobs) == 0) {
    message("No CI jobs were launched. A user validation might be required on your Gitlab account. To use free CI/CD minutes on shared runners, you\u2019ll need to validate your account with a credit card. If you prefer not to provide one, you can run pipelines by bringing your own runners and disabling shared runners for your project.")

    return(NULL)
  }

  while (jobs$status %in% c("created", "running", "pending")) {
    cat_rule("Waiting for the job to finish")
    Sys.sleep(10)
    jobs <- gitlab(
      req = paste0("projects/", project_id, "/jobs"),
      verb = httr::GET
    )[
      1,
    ]
  }

  Sys.sleep(3)
  ## Test deploy on Connect here, can we access the app?
  app_name <- gsub(
    x = unique_project_name,
    pattern = "\\.",
    replacement = "-"
  )

  connect_status <- fetch_connect(
    connect_api_token = connect_api_token,
    connect_url = connect_url,
    app_name = app_name
  )

  jobs["connect"] <- connect_status[["status"]]


  ## Delete the app on Connect if a guid is available
  on.exit(
    {
      guid_is_valid <- str_detect(
        string = connect_status[["guid"]],
        pattern = "[a-z0-9-]{36}"
      )

      if (isTRUE(guid_is_valid)) {
        httr::DELETE(
          sprintf(
            "%s/__api__/v1/content/%s",
            connect_url,
            connect_status[["guid"]]
          ),
          add_headers(Authorization = paste(
            "Key",
            connect_api_token
          ))
        )
      }
    },
    add = TRUE
  )
  return(jobs)
}

#' @noRd
get_or_create_var_env_gitlab <- function(
  project_id,
  var_env,
  value
    ) {
  exist_var_env <- try(
    gitlab(
      req = paste0("projects/", project_id, "/variables/", var_env),
      verb = httr::GET
    ),
    silent = TRUE
  )

  if (inherits(exist_var_env, "try-error")) {
    test_404 <- grepl("404", exist_var_env)
    if (!test_404) {
      stop("Cannot access to the repo to check env var")
    }
  }

  # create var env if 404

  gitlab(
    req = paste0("projects/", project_id, "/variables/"),
    key = var_env,
    value = value,
    verb = httr::POST
  )
}
```

```{r example-with_gitlab_project, eval=FALSE}
#' \dontrun{
output <- with_gitlab_project(
  gitlab_url = Sys.getenv("GITLAB_URL", unset = "https://gitlab.com"),
  namespace_id = NULL,
  project_name = "lozen.test.project",
  exp = {
    bookdown::create_bs4_book(path = ".")
    bookdown::render_book()
    lozen::use_gitlab_ci(
      type = "bookdown"
    )
  }
)
output
#' }
```

```{r tests-with_gitlab_project}
test_that("with_gitlab_project works", {
  # TODO - Remove ; allow test to pass on CI
  skip_on_ci()

  if (Sys.getenv("ALLOW_CI_TESTS_ON_GITLAB", unset = "FALSE") == "TRUE") {
    output <- with_gitlab_project(
      gitlab_url = Sys.getenv("GITLAB_URL", unset = "https://gitlab.com"),
      namespace_id = NULL,
      project_name = "lozen.test.project",
      exp = {
        bookdown::create_bs4_book(path = ".")
        bookdown::render_book()
        lozen::use_gitlab_ci(
          type = "bookdown"
        )
      }
    )

    if (is.null(output)) {
      message("No CI jobs were launched. A user validation might be required on your Gitlab account. To use free CI/CD minutes on shared runners, you\u2019ll need to validate your account with a credit card. If you prefer not to provide one, you can run pipelines by bringing your own runners and disabling shared runners for your project.")
    } else {
      expect_equal(
        output$status,
        "success"
      )
    }
  }
})
```

## Subfunction : `fetch_connect()`

This function will be triggered during a call to `with_gitlab_project()` to check whether the app has been correctly deployed on connect.

It requires an API key to Connect. It will return the HTTP status code and the guid of the app that will be used to delete the app on function exit.

```{r function-fetch_connect}
#' fetch_connect
#'
#' Fetch deployment status on Connect of a given app
#'
#' @param app_name character Name of the app to be fetched
#' @param connect_api_token character API token to enable access to Connect
#' @param connect_url character URL to Connect server
#'
#' @importFrom httr GET add_headers content status_code
#' @importFrom purrr map_df
#' @importFrom tibble tibble
#' @importFrom dplyr filter pull
#'
#' @return list A list containing the HTTP code status and the guid of the app
#'
#' @export
fetch_connect <- function(
  app_name,
  connect_api_token = Sys.getenv("CONNECT_TOKEN"),
  connect_url = Sys.getenv("CONNECT_URL")
    ) {
  stopifnot("connect_api_token is missing" = isTRUE(connect_api_token != ""))
  stopifnot("connect_url is missing" = isTRUE(connect_url != ""))


  # Search Connect for content id
  result <- GET(
    sprintf(
      "%s/__api__/v1/content",
      connect_url
    ),
    add_headers(Authorization = paste("Key", connect_api_token))
  )

  # Search for app matching the input name
  selected_apps <- result |>
    content() |>
    purrr::map_df(
      ~ tibble::tibble(
        guid = .x$guid,
        name = .x$name,
      )
    ) |>
    dplyr::filter(
      name == app_name
    )

  # Return job fail if app is not found
  if (nrow(selected_apps) == 0) {
    message(sprintf("The app %s is not found on Connect server", app_name))
    return(
      list(
        "status" = "no app found",
        "guid" = ""
      )
    )
  } else {
    # Return HTTP request status if app is found
    app_guid <- selected_apps[1, ] %>%
      dplyr::pull(guid)

    result <- GET(
      sprintf(
        "%s/connect/#/apps/%s/access",
        connect_url,
        app_guid
      ),
      add_headers(Authorization = paste("Key", connect_api_token))
    )

    return(
      list(
        "status" = status_code(result),
        "guid" = app_guid
      )
    )
  }
}
```
  
```{r example-fetch_connect, eval = FALSE}
#' \dontrun{
fetch_connect(app_name = "my_app_name")
#' }
```
  
```{r tests-fetch_connect}
test_that("fetch_connect works", {
  skip_if_not(isTRUE(Sys.getenv("CONNECT_TOKEN") != ""))
  skip_if_not(isTRUE(Sys.getenv("CONNECT_URL") != ""))

  expect_message(
    object = fetch_connect(app_name = "this-app-does-not-exist"),
    regexp = "The app this-app-does-not-exist is not found on Connect server"
  )



  lozen_infos <- fetch_connect(
    app_name = "lozen-pkgdown-website"
  )

  expect_equal(
    object = lozen_infos[["status"]],
    expected = 200
  )

  expect_equal(
    object = lozen_infos[["guid"]],
    expected = "5e89ed9a-f63b-4b5c-8268-d898579419ef"
  )
})
```


```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(
  flat_file = "dev/flat_helper_testthat.Rmd",
  vignette_name = "cb - Testthat tools",
  overwrite = TRUE,
  check = FALSE,
  document = FALSE,
  open_vignette = FALSE
)

rstudioapi::navigateToFile(
  # Go to the dev_history_package.Rmd to inflate all flat files
  "dev/dev_history_package.Rmd",
  line = 170
)
```

