---
title: "Manipulate a GitHub project"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
library(glue)
library(gh)
library(yesno)
library(gert)
library(dplyr)
library(gitlabr)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

# Create the project

## `create_group_project_github()`: Create a new project on GitHub

Create a new project on GitHub if it does not already exist.

```{r function-create_group_project_github}
#' Create new project on GitHub
#'
#' @param repo name of the project to create
#' @param owner Owner of the repo
#'
#' @importFrom gh gh
#' @importFrom glue glue
#' @importFrom yesno yesno
#'
#' @return project_id. Side effect: Create a project on GitHub if not exists.
#'
#' @export
#'
create_group_project_github <- function(repo, owner) {
  repo_exists <- try(gh(glue("/repos/{owner}/{repo}")), silent = TRUE)

  if (!inherits(repo_exists, "try-error")) {
    message("Project: '", repo, "' already exists in group: ", owner)
  } else {
    # Create project
    # my_project <- gh(glue("POST /repos/{owner}/{repo}"))
    # project_id <- my_project$id
    # message("New project created: ", project_id)
    yesno::yesno(glue("You need to create the repository yourself. Did you created {owner}/{repo} ?"))
  }

  glue("{owner}/{repo}")
  # as.numeric(project_id)
}
```

```{r examples-create_group_project_github, eval = FALSE}
#' \dontrun{
create_group_project_github(
  repo = "areponame",
  owner = "ghowner"
)
#' }
```

```{r tests-create_group_project_github}
test_that("create_group_project_github works", {
  expect_true(inherits(create_group_project_github, "function"))
})
```


# Create the board

## `add_board_github()`: Add a Board to the GitHub project

Add a Board to the GitHub project with the default columns :

- Open
- Blocked
- Meta
- Ready
- In Progress
- Review
- Validation

```{r function-add_board_github}
#' add_board_github
#'
#' @param owner Owner of the repository
#' @param repo Repository name
#' @param columns Names of columns to create in the Board
#'
#' @importFrom gh gh
#' @importFrom gitlabr multilist_to_tibble
#' @importFrom glue glue
#'
#' @export
add_board_github <- function(owner,
                             repo,
                             columns = c("Open", "Blocked", "Meta", "Ready", "In Progress", "Review", "Validation")) {
  board <- gh::gh(glue("POST /repos/{owner}/{repo}/projects"),
    name = "Development"
  )

  board <- multilist_to_tibble(board)
  project_id <- board[["id"]]

  # Add columns
  for (the_col in columns) {
    gh::gh(glue("POST /projects/{project_id}/columns"),
      name = the_col
    )
    message(glue("Column '{the_col}' created"))
  }
}
```

```{r example-add_board_github, eval = FALSE}
#' \dontrun{
add_board_github(
  owner = "ghowner",
  repo = "areponame"
)
#' }
```

```{r tests-add_board_github}
test_that("add_board_github works", {
  expect_true(inherits(add_board_github, "function"))
})
```


# Create the Wiki

## `add_wikis_github()`: Add the Wikis

Add wiki pages to the project. You can select multiple pages with the `type` parameter among `home`, `cr`, `keys` and `weekly`.
    
```{r function-add_wikis_github}
#' add_wikis_github
#'
#' @param owner Owner of the repository
#' @param repo Repository name
#' @param type Wiki type to add
#'
#' @importFrom glue glue
#' @importFrom yesno yesno
#' @importFrom gert git_clone git_pull git_add git_commit git_push
#'
#'
#' @export
add_wikis_github <- function(owner,
                             repo, type = c("home", "cr", "keys", "weekly")) {
  type <- match.arg(type, several.ok = TRUE)

  tempwiki <- tempfile(pattern = "wiki")
  wikigit <- glue("https://github.com/{owner}/{repo}.wiki.git")

  wiki_clone <- try(gert::git_clone(url = wikigit, path = tempwiki), silent = TRUE)

  if (!inherits(wiki_clone, "try-error")) {
    message("There already are some wikis")
    # existing wiki are cloned
    # existing_wiki <- gh(req = paste0("projects/", project_id, "/wikis"),
    #                     verb = httr::GET)
  } else {
    yesno::yesno("You need to create a Wiki Home Page on GitHub.com first. Is it done now?")

    wiki_clone <- try(gert::git_clone(url = wikigit, path = tempwiki), silent = TRUE)

    existing_wiki <- list.files(wiki_clone)
    #
    # existing_wiki <- tibble(name = character(0))
    # usethis::create_project(tempwiki, open = FALSE)
    # usethis::with_project(path = tempwiki, {
    #   usethis::use_git()
    #   usethis::use_git_remote(url = wikigit)
    # })
  }

  if ( # "home.md" %in% tolower(existing_wiki) &
    "home" %in% type) {
    gert::git_pull(repo = tempwiki)

    # Always home
    wiki <- readLines(system.file("github", "wiki_home.md", package = "lozen"))
    # Changer {repo}
    wiki <- gsub(pattern = "\\{repo\\}", replacement = repo, x = wiki)
    # Changer {owner}
    wiki <- gsub(pattern = "\\{owner\\}", replacement = owner, x = wiki)

    # Home
    writeLines(wiki, file.path(tempwiki, "Home.md"))
    # rstudioapi::openProject(path = tempwiki, newSession = TRUE)
    gert::git_add(files = c("Home.md", "*.Rproj"), repo = tempwiki)
    gert::git_commit(message = "Update Home wiki", repo = tempwiki)

    gert::git_push(repo = tempwiki)

    message("Wiki home page added")
  }

  if ("cr" %in% type) {
    gert::git_pull(repo = tempwiki)

    # Comptes-rendus
    wiki2 <- readLines(system.file("github", "wiki_cr.md", package = "lozen"))

    # Changer {date}
    wiki2 <- gsub(pattern = "\\{date\\}", replacement = Sys.Date(), x = wiki2)

    # Home
    writeLines(wiki2, file.path(tempwiki, "comptes-rendus.md"))
    # rstudioapi::openProject(path = tempwiki, newSession = TRUE)
    gert::git_add(files = c("comptes-rendus.md", "*.Rproj"), repo = tempwiki)
    gert::git_commit(message = "Add comptes-rendus wiki", repo = tempwiki)

    gert::git_push(repo = tempwiki)

    message("Wiki Comptes-rendus page added")
  }

  if ("keys" %in% type) {
    gert::git_pull(repo = tempwiki)

    # Comptes-rendus
    wiki3 <- readLines(system.file("github", "wiki_keys.md", package = "lozen"))
    # Changer {mon_projet}
    wiki3 <- gsub(pattern = "\\{date\\}", replacement = Sys.Date(), x = wiki3)

    writeLines(wiki3, file.path(tempwiki, "Key_Dates.md"))
    # rstudioapi::openProject(path = tempwiki, newSession = TRUE)
    gert::git_add(files = c("Key_Dates.md", "*.Rproj"), repo = tempwiki)
    gert::git_commit(message = "Add Key Dates wiki", repo = tempwiki)

    gert::git_push(repo = tempwiki)

    message("Wiki 'Key dates' page added")
  }

  if ("weekly" %in% type) {
    gert::git_pull(repo = tempwiki)

    # Comptes-rendus
    # wiki3 <- readLines(system.file("github", "wiki_keys.md", package = "lozen"))
    # Changer {mon_projet}
    # wiki3 <- gsub(pattern = "\\{date\\}", replacement = Sys.Date(), x = wiki3)

    cat("# Weekly", file = file.path(tempwiki, "Weekly.md"))
    # writeLines(wiki3, file.path(tempwiki, "Key_Dates.md"))
    # rstudioapi::openProject(path = tempwiki, newSession = TRUE)
    gert::git_add(files = c("Weekly.md", "*.Rproj"), repo = tempwiki)
    gert::git_commit(message = "Add Weekly wiki", repo = tempwiki)

    gert::git_push(repo = tempwiki)

    message("Wiki 'Key dates' page added")
  }
}
```
  
```{r example-add_wikis_github, eval = FALSE}
#' \dontrun{
add_wikis_github(
  owner = "ghowner",
  repo = "areponame"
)
#' }
```

```{r tests-add_wikis_github}
test_that("add_wikis_github works", {
  expect_true(inherits(add_wikis_github, "function"))
})
```


```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(
  flat_file = "dev/flat_manage_github_projects.Rmd",
  vignette_name = NA,
  overwrite = TRUE,
  check = FALSE,
  document = FALSE,
  open_vignette = FALSE
)

rstudioapi::navigateToFile( # Go to the dev_history_package.Rmd to inflate all flat files
  "dev/dev_history_package.Rmd",
  line = 170
)
```
