---
title: "flat_build_pkgdown_with_reports.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
library(testdown)
library(pkgdown)
library(fs)
library(knitr)
library(gitdown)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

# `build_pkgdown_with_reports()` : build a pkgdown with coverage and test reports

This function will generate the pkgdown of the current package using `{pkgdown}`, together with the `{covr}` and `{testdown}` reports. These reports will be embedded inside the pkgdown and accessible through the navigation bar. It requires the functions `covr::report()`, `testdown::test_down`, `gitdown::git_down` that are suggested package imports from `{lozen}`.

```{r function-build_pkgdown_with_reports}
#' Build a pkgdown with extra reports tab for testdown and coverage output
#'
#' @importFrom fs dir_create file_move
#' @importFrom pkgdown build_site
#'
#' @param pkg character The path to the package to be build and reported
#' @param pkgdown_path character The relative path inside the package to store the final site
#' @param assets_path character The relative path within the package to store the reports outputs
#' @param reports character A vector of reports to be produced, can be any subset of `c("testdown","coverage")`
#' @param git_branch_ref character A vector of the git branch to use, 'main' by default
#' @param overwrite_assets logical Whether the assets directory to store reports should be overwritten
#'
#' @return None Generate a pkgdown with test and coverage reports
#' @export
build_pkgdown_with_reports <- function(pkg = ".",
                                       pkgdown_path = "public",
                                       assets_path = "pkgdown/assets",
                                       reports = c("coverage", "testdown", "gitdown"),
                                       git_branch_ref = "main",
                                       overwrite_assets = TRUE) {
  # Selected reports
  reports <- match.arg(
    arg = reports,
    several.ok = TRUE
  )

  # clear assets dir if needed
  if (isTRUE(overwrite_assets)) {
    unlink(file.path(pkg, assets_path), recursive = TRUE)
  }

  # initialize navbar report
  menu <- list()
  if (length(reports) != 0) {
    dir_create(file.path(pkg, assets_path))
  }

  # generate covr report in a tmp folder and move it to assets path
  if (isTRUE("coverage" %in% reports)) {
    if (!requireNamespace("covr", quietly = TRUE)) {
      stop(
        "{covr} needs to be installed for",
        " `lozen::build_pkgdown_with_reports(reports = 'coverage')`",
        " to use `covr::report()`."
      )
    }
    if (!requireNamespace("DT", quietly = TRUE)) {
      stop(
        "{DT} needs to be installed for",
        " `lozen::build_pkgdown_with_reports(reports = 'coverage')`",
        " to use `covr::report()`."
      )
    }
    if (!requireNamespace("htmltools", quietly = TRUE)) {
      stop(
        "{htmltools} needs to be installed for",
        " `lozen::build_pkgdown_with_reports(reports = 'coverage')`",
        " to use `covr::report()`."
      )
    }
    if (!requireNamespace("markdown", quietly = TRUE)) {
      stop(
        "{markdown} needs to be installed for",
        " `lozen::build_pkgdown_with_reports(reports = 'coverage')`",
        " to use `markdown::markdownToHTML()`."
      )
    }
    covr_pkg <- covr::package_coverage(path = pkg)
    covr::report(
      x = covr_pkg,
      file = file.path(assets_path, "coverage", "coverage.html"),
      browse = FALSE
    )

    # file_move(file.path(pkg, "coverage"), file.path(assets_path, "coverage"))
    menu[[length(menu) + 1]] <- list(text = "coverage", href = "coverage/coverage.html")
    # Add coverage explanation
    markdown::markdownToHTML(
      file = system.file("package", "codecoverage_explanation.md",
        package = "lozen"
      ),
      output = file.path(assets_path, "coverage", "codecoverage_explanation.html")
    )
    menu[[length(menu) + 1]] <- list(
      text = "coverage explained",
      href = "coverage/codecoverage_explanation.html"
    )
  }

  # generate testdown report in assets path
  if (isTRUE("testdown" %in% reports)) {
    if (!requireNamespace("testdown", quietly = TRUE)) {
      stop(
        "{testdown} needs to be installed for",
        " `lozen::build_pkgdown_with_reports(reports = 'testdown')`",
        " to use `testdown::test_down()`."
      )
    }

    testdown::test_down(
      pkg = pkg,
      book_path = file.path(assets_path, "testdown"),
      open = FALSE
    )
    menu[[length(menu) + 1]] <- list(text = "testdown", href = "testdown/index.html")
  }

  # generate gitdown report in assets path
  if (isTRUE("gitdown" %in% reports)) {
    if (!requireNamespace("gitdown", quietly = TRUE)) {
      stop(
        "{gitdown} needs to be installed for",
        " `lozen::build_pkgdown_with_reports(reports = 'gitdown')`",
        " to use `gitdown::git_down()`."
      )
    }

    gitdown::git_down(
      repo = pkg,
      book_path = file.path(assets_path, "gitdown"),
      ref = git_branch_ref,
      open = FALSE
    )
    homepage <- file.path(
      "gitdown",
      list.files(
        pattern = "^gitbook-for",
        file.path(assets_path, "gitdown")
      )[1]
    )
    menu[[length(menu) + 1]] <- list(text = "gitdown", href = homepage)
  }

  # prepare yaml settings to add reports in navbar
  yaml_settings <- list(
    destination = pkgdown_path,
    template = list(
      assets = assets_path
    ),
    navbar = list(
      structure = list(
        left = c("intro", "reference", "articles", "tutorials", "news", "reports")
      ),
      components = list(
        reports = list(
          text = "Reports",
          menu = menu
        )
      )
    )
  )

  # build site without preview
  build_site(
    pkg = pkg,
    override = yaml_settings,
    preview = FALSE
  )
}
```

```{r examples-build_pkgdown_with_reports, eval = FALSE}
#' \dontrun{
# build_pkgdown_with_reports(
#    pkg = ".",
#    pkgdown_path = "public",
#    assets_path = "pkgdown/assets",
#    reports = c("testdown","coverage")
#' }
```


```{r tests-build_pkgdown_with_reports}
test_that("build_pkgdown_with_reports works", {
  # create tmp folder
  tmppkg <- tempfile(pattern = "pkg-")
  dir.create(tmppkg)
  # Copy fake package from attachment in "inst/" for {lozen}
  # file.copy(
  #   system.file("dummypackage", package = "attachment"),
  #   "inst/dummypackage",
  #   recursive = TRUE
  # )
  file.copy(
    system.file("dummypackage", package = "lozen"),
    tmppkg,
    recursive = TRUE
  )
  path <- file.path(tmppkg, "dummypackage")

  # Add _pkgdown.yml file for tests
  if (requireNamespace("thinkrtemplate", quietly = TRUE)) {
    cat("template:\n  package: thinkrtemplate\n", file = file.path(path, "_pkgdown.yml"))
    cat("^_pkgdown\\.yml$\n", file = file.path(path, "Rbuildignore"))
  }

  if (requireNamespace("testdown", quietly = TRUE)) {
    # Test testdown ----
    build_pkgdown_with_reports(
      pkg = path,
      pkgdown_path = file.path(path, "public"),
      assets_path = file.path(path, "pkgdown/assets"),
      reports = c("testdown")
    )

    # Browse interactively
    # browseURL(file.path(path, "public", "index.html"))

    # Test file are correctly created in pkgdown and public folders
    # ignore libs
    expect_setequal(
      object = list.files(file.path(path, "pkgdown", "assets", "testdown")),
      expected = c(
        "_bookdown.yml", "_output.yml", "404.html", "aggregated-failures-and-errors.html",
        "aggregated-skipped.html", "aggregated-warnings.html", "global-results-for-package-dummypackage.html",
        "how-to-read-this-report.html", "index.html", "libs", "style.css",
        "test-addition.html", "testdown-report-for-dummypackage.html"
      )
    )
    expect_true(
      all(
        c(
          "404.html", "articles", "authors.html",
          # "deps",
          "index.html",
          # "LICENSE-text.html", "LICENSE.html", # if package with license
          "link.svg", "pkgdown.js",
          "pkgdown.yml", "reference",
          # "search.json", # Bootstrap > 5.0
          "sitemap.xml", "testdown"
        ) %in%
          list.files(file.path(path, "public"))
      )
    )

    # Test navbar is correctly set with testdown url
    expect_true(
      any(grepl("<a href=\"testdown/index.html\">testdown</a>", readLines(file.path(path, "public", "index.html"))))
    )
  }

  if (requireNamespace("covr", quietly = TRUE)) {
    # Test coverage ----
    # Note : potential check issues :
    # https://github.com/r-lib/covr/tree/84836b3f2267d861b4110570e221dd7a418a9787#why-cant-covr-run-during-r-cmd-check
    build_pkgdown_with_reports(
      pkg = path,
      pkgdown_path = file.path(path, "public"),
      assets_path = file.path(path, "pkgdown/assets"),
      reports = "coverage"
    )

    # Browse interactively
    # browseURL(file.path(path, "public", "index.html"))

    expect_true(
      all(c(
        "codecoverage_explanation.html",
        "coverage.html"
      ) %in%
        list.files(file.path(path, "pkgdown", "assets", "coverage")))
    )

    # Navbar
    expect_true(
      any(grepl(
        "<a href=\"coverage/coverage.html\">coverage</a>",
        readLines(file.path(path, "public", "index.html"))
      ))
    )
    expect_true(
      any(grepl(
        "<a href=\"coverage/codecoverage_explanation.html\">coverage explained</a>",
        readLines(file.path(path, "public", "index.html"))
      ))
    )
  }

  # # The repo is not a git repository (yet?)
  # build_pkgdown_with_reports(
  #   pkg = path,
  #   pkgdown_path = file.path(path, "public"),
  #   assets_path = file.path(path, "pkgdown/assets"),
  #   reports = "gitdown"
  # )

  # Clean
  unlink(path, recursive = TRUE)
})
```


```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(
  flat_file = "dev/flat_build_pkgdown_with_reports.Rmd",
  vignette_name = "af - Build a pkgdown with reports",
  overwrite = TRUE,
  check = FALSE,
  document = FALSE,
  open_vignette = FALSE
)

rstudioapi::navigateToFile( # Go to the dev_history_package.Rmd to inflate all flat files
  "dev/dev_history_package.Rmd",
  line = 170
)
```

