---
output: 
  github_document:
    toc: true
    toc_depth: 3
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## Development

### Tokens

#### GitLab

- Create a personal access token on GitLab, with the rights: "read_repository", "write_repository", "api", "read_api"
- Save the token in your `.Renviron` under the name `GITLAB_TOKEN`
- Save the url of your gitlab, if it is not `gitlab.com`, in your `.Renviron` under the name `GITLAB_URL`
- Set up your git user email and git user name :

```{r, eval=FALSE}
usethis::use_git_config(scope = "user",
                        user.name = "username", 
                        user.email = "user@email.fr")
```

- To try functions that manipulate connect :
    - You have to set up at `TRUE` the env variable `ALLOW_CI_TESTS_ON_GITLAB`
    - Set up a token for connect with `CONNECT_TOKEN`
    - Set up a url for connect with `CONNECT_URL`
    - Set up your username for connect with `CONNECT_USER`


#### GitHub

- Create a personal access token on GitHub
- Save the token in your `.Renviron` under the name `GITHUB_PAT`

- For unit tests, you will have to set up to `TRUE` the env variable `ALLOW_PUBLISHING_ON_GITHUB`


