---
title: "ad - Set up continuous integration and continuous deployment for Gitlab CI/CD"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ad-set-up-continuous-integration-and-deployment-through-gitlab-ci}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lozen)
```

# Initiate the Continuous Integration (CI) / Continuous Deployment (CD) 

These operations will set up on Gitlab :
- the continuous integration of your project
- the continuous deployment, on Gitlab Pages, of your pkgdown (if you are working with a R package or a golem app) or of your bookdown.

A `.gitlab-ci.yml` file will be created at the root of your project. Please ensure that this file will be pushed on your repository for the CI/CD to be working.

Please note that any `.gitlab-ci.yml` file already present would be overwritten.

## For a R package or a {golem} app

```{r eval = FALSE}
lozen::use_gitlab_ci(
  project_path = project_path,
  type = "check-coverage-pkgdown"
)
```

Please note that the `R/` and `tests/` folders will be missing from a R package created using `create_r_project(type = "package")`. If these folders remains missing, the "coverage" job of the "test" stage of the CI pipeline will fail (the following steps of the CI pipeline will nevertheless be run). 

## For a book 

```{r eval = FALSE}
lozen::use_gitlab_ci(
  project_path = project_path,
  type = "bookdown"
)
```


## How can I find the pkgdown/book associated with my project

Once the former steps are done, you can commit all your changes and push them to your repository remote.

Thereafter, you should be able to [see your pipeline running](https://docs.gitlab.com/ee/ci/pipelines/#view-pipelines) on Gitlab.

If your pipeline did not raise any error, the deployed pkgdown/book is now hosted on [Gitlab pages](https://docs.gitlab.com/ee/user/project/pages/getting_started_part_one.html).

If you are working on `https://gitlab.com`, the url should be `https://username.gitlab.io/your.repository.name`. 


# Continuous deployment on Posit Connect

## CD of a pkgdown

For the following to be working, please ensure you are working in a valid R package. Your project must be associated with a repository present on Gitlab.

Before running the following commands please ensure that you are working on your R package project.

### Create the pkgdown

```{r, eval=FALSE}
usethis::use_pkgdown()
pkgdown::build_site(override = list(destination = "inst/site"))
```

### Initiate the deployment of your pkgdown

#### To be done on your R project

```{r, eval=FALSE}
lozen::use_gitlab_ci_deploy_connect_pkgdown()
```

Any `.gitlab-ci.yml` file already present in your project is now completed with new staged, specific to the deployment on Connect.

Be aware that running this command multiple times would duplicate these steps in your `.gitlab-ci.yml` file. It should be avoided.

#### To be done on Gitlab

Some environment variables must be set on Gitlab for the CI/CD to be working.

You'll need to define : 

```{r, eval=FALSE}
CONNECT_URL <- "https://my.connect.url"
CONNECT_NAME <- "my.connect.server.name"
CONNECT_USER <- "my.connect.username"
CONNECT_TOKEN <- "my.api.key.generated.in.connect"
APP_NAME <- "the.name.of.your.pkgdown.on.connect"
# APP_NAME is not mandatory; whether it is not provided, it will be replaced by the name of your project on Gitlab
```

For most of them, you may have already set them on your `.Renviron` file (see the dedicated section on the {lozen} README).

If you are not familiar with defining environement variable on gitlab, please follow the [official documentation](https://docs.gitlab.com/ee/ci/variables/index.html).

Once this is done, you can commit all your changes and push them to your repository remote.

Thereafter, you should be able to [see your pipeline running](https://docs.gitlab.com/ee/ci/pipelines/#view-pipelines) on Gitlab.

#### How can I find the pkgdown associated with my R package on Posit Connect

If your pipeline did not raise any error, you app is now deployed on your Posit Connect. You can now log in your Posit Connect and enjoy your pkgdown !


## CD of a golem shiny app

For the following to be working, please ensure you are working in a shiny app initiated with {golem}. Your app project must be associated with a repository present on Gitlab.

If this is not done yet please go to the vignette `vignettes/aa-create-a-new-project-with-gitlab.Rmd` and follow the steps related to the creation of a project on Gitlab and of a R project skeleton.

Before running the following commands please ensure that you are working on your golem app project.

### Add an app.R at the root of your package to deploy on RStudio Connect 

```{r, eval=FALSE}
golem::add_rstudioconnect_file()
```

### Initiate the deployment of your app

#### To be done on your R project

```{r, eval=FALSE}
use_gitlab_ci_deploy_connect_shiny()
```

Any `.gitlab-ci.yml` file already present in your project is now completed with new staged, specific to the deployment on Connect.

Be aware that running this command multiple times would duplicate these steps in your `.gitlab-ci.yml` file. It should be avoided.

#### To be done on Gitlab

Some environment variables must be set on Gitlab for the CI/CD to be working.

You'll need to define : 

```{r, eval=FALSE}
CONNECT_URL <- "https://my.connect.url"
CONNECT_NAME <- "my.connect.server.name"
CONNECT_USER <- "my.connect.username"
CONNECT_TOKEN <- "my.api.key.generated.in.connect"
APP_NAME <- "the.name.of.your.app.on.connect"
# APP_NAME is not mandatory; whether it is not provided, it will be replaced by the name of your project on Gitlab
```

For most of them, you may have already set them on your `.Renviron` file (see the dedicated section on the {lozen} README).

If you are not familiar with defining environement variable on gitlab, please follow the [official documentation](https://docs.gitlab.com/ee/ci/variables/index.html).

Once this is done, you can commit all your changes and push them to your repository remote.

Thereafter, you should be able to [see your pipeline running](https://docs.gitlab.com/ee/ci/pipelines/#view-pipelines) on Gitlab.

#### How can I find the app associated with my {golem} package

If your pipeline did not raise any error, you app is now deployed on your Posit Connect. You can now log in your Posit Connect and enjoy your app !


## CD of a book

#### --TO-BE-COMPLETED
